---
title: "Bookings Recorded by Carroll"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  dev = "ragg_png",
  cache = FALSE
  )

source("data_cleaning/00_library.R")
source("data_cleaning/01_functions.R")
source("data_cleaning/01_functions_visuals.R")
source("data_cleaning/rdas.R")
```

Caroll provided two files, bookings and releases. Not using releases file. 

Booking Types:    

ADULT ORDER OF COMMITMENT
ARREST WARRANT 
BAIL ORDER (CIRCUIT/SUPERIOR)
CAPIAS
CONVERTED DOCUMENT
COURT COMMITTED 
DETAINEE REQUEST
DETENTION ORDER      
ELECTRONIC BENCH WARRANT            
PROTECTIVE CUSTODY

Sentence Statuses:  

AWAITING TRIAL
BAIL SET
BOND DENIED
DETAINER
DISMISSED
HELD
PRE-TRIAL 
PROTECTIVE CUSTODY 
SENTENCE SUSPENDED 
SENTENCED
SENTENCED FINES
STATE PRISONER 

<br>

# Overview 

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           #charge_desc,
           booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_booking_recordings(data1))
```

<br>

### ADULT ORDER OF COMMITMENT 

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "ADULT ORDER OF COMMITMENT") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### ARREST WARRANT   

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "ARREST WARRANT") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### BAIL ORDER (CIRCUIT/SUPERIOR)  

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "BAIL ORDER (CIRCUIT/SUPERIOR)") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### CAPIAS  

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "CAPIAS") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### CONVERTED DOCUMENT  

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "CONVERTED DOCUMENT") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### COURT COMMITTED  

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "COURT COMMITTED") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### DETAINEE REQUEST  

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "DETAINEE REQUEST") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### DETENTION ORDER  

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "DETENTION ORDER") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### ELECTRONIC BENCH WARRANT  

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "ELECTRONIC BENCH WARRANT") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### PROTECTIVE CUSTODY  

```{r}
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "PROTECTIVE CUSTODY") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>
<br>

