---
title: "Bookings Recorded by Hillsborough"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  dev = "ragg_png",
  cache = FALSE
  )

source("data_cleaning/00_library.R")
source("data_cleaning/01_functions.R")
source("data_cleaning/01_functions_visuals.R")
source("data_cleaning/rdas.R")
```

Booking Types:  

ADMINISTRATIVE TRANSFER  
CAPIAS  
CONVICTED  
DETAINERS,WARRANTS,HOLDS  
DRUG COURT  
FROM COURT-SENTENCED  
FROM COURT-SENTENCED WEEKENDS  
FROM COURT PRE TRIAL   
HOLD FOR ANOTHER AGENCY  
NEW ARREST  
PRETRIAL PROBATION/PAROLE (VIOLATION/DETENTION ORDER)   
PROTECTIVE CUSTODY  
SENTENCED/SENTENCING  
TREATMENT AND SERVICES    

Sentence Statuses:   

CONVICTED
CONVICTED ROCK
PRE TRIAL DRUG COURT (MANCH)
PRE TRIAL DRUG COURT (NASHUA) 
PRE TRIAL ROCK SATCO
PRETRIAL
PRETRIAL BELKNAP
PRETRIAL CARROLL 
PRETRIAL COOS
PRETRIAL DRUG COURT SATCO
PRETRIAL GRAFTON
PRETRIAL GRAFTON SATCO 
PRETRIAL MERRIMACK
PRETRIAL ROCK
PRETRIAL SATCO
PRETRIAL SULLIVAN 
SENTENCED 
SENTENCED-HSC NORTH DRUG COURT SANCTION 
SENTENCED-HSC SOUTH DRUG COURT SANCTION
SENTENCED MERRIMACK 
SENTENCED ROCK
SENTENCED ROCK SATCO
SENTENCED SATCO
SENTENCED SULLIVAN 
SENTENCED W/HOLD
SENTENCED W/HOLD MERRIMACK
SENTENCED W/HOLD ROCK
SENTENCED W/HOLD SATCO 
SENTENCED WALK IN
SENTENCED WEEKENDER
SENTENCED WEEKENDER W/HOLD
STATE INMATE 
TREATMENT AND SERVICES 

<br>

# Overview

```{r}
data1 <- SAVE_adm_all %>%
  filter(county == "Hillsborough") %>%
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           #charge_desc,
           booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_booking_recordings(data1))
```

<br>
