---
title: "Booking Types Recorded by County"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  dev = "ragg_png",
  cache = FALSE
  )

source("data_cleaning/00_library.R")
source("data_cleaning/01_functions.R")
source("data_cleaning/01_functions_visuals.R")
source("data_cleaning/rdas.R")
```

# Booking Type Categories

1. ADMINISTRATIVE TRANSFER  
2. DETAINERS, WARRANTS, HOLDS   
3. DUAL   
4. NH STATE PRISONER   
5. PRETRIAL   
6. PROTECTIVE CUSTODY   
7. SENTENCED/SENTENCING    

<br>

# Carroll 

Caroll provided two files, bookings and releases.  

```{r}
# Carroll has charge descriptions, codes (sometimes),and booking types
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           #charge_desc,
           booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_booking_recordings(data1))
```

You can see in the table above that some protective custody holds were recorded in the booking type OR the charge description, which means the booking type was either pretrial or protective custody. The booking type should always be protective custody holds in these cases so the booking type was standardized.

<br>

### Administrative Transfer

```{r}
# Carroll has charge descriptions, codes (sometimes),and booking types
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "ADMINISTRATIVE TRANSFER") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### Detainers, Warrants, Holds

```{r}
# Carroll has charge descriptions, codes (sometimes),and booking types
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "DETAINERS, WARRANTS, HOLDS") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### Dual

Does dual mean that they were booked for multiple reasons?

```{r}
# Carroll has charge descriptions, codes (sometimes),and booking types
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "DUAL") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### NH State Prisoner

```{r}
# Carroll has charge descriptions, codes (sometimes),and booking types
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "NH STATE PRISONER") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### Pretrial

```{r}
# Carroll has charge descriptions, codes (sometimes),and booking types
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "PRETRIAL") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### Protective Custody

```{r}
# Carroll has charge descriptions, codes (sometimes),and booking types
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "PROTECTIVE CUSTODY") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>

### Sentences/Sentencing

```{r}
# Carroll has charge descriptions, codes (sometimes),and booking types
data1 <- adm_all %>%
  filter(county == "Carroll") %>%
  filter(booking_type_standard == "DETAINERS, WARRANTS, HOLDS") %>% 
  select(id,
         booking_id,
         charge_code,
         charge_desc,
         booking_type,
         booking_type_standard,
         sentence_status,
         release_type
         ) %>%
  distinct() %>%
  group_by(#charge_code,
           charge_desc,
           #booking_type,
           booking_type_standard,
           sentence_status,
           release_type) %>%
  summarise(total = n()) %>% 
  arrange(booking_type_standard)

# Custom function for booking recordings table
# Shows how each county records things differently
(table1 <- fnc_reactable_charges_booking_recordings(data1))
```

<br>
<br>















