---
title: "Data Dictionary"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales","raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","csgjcr","distill","ezknitr")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  dev = "ragg_png",
  cache = FALSE
  )
```

```{r include=FALSE}
### set theme
theme_set(theme_minimal())

# load packages and pull data to create codebooks
source("data_cleaning/00_library.R")
source("data_cleaning/01_functions.R")
source("data_cleaning/02_import.R")
source("data_cleaning/03_belknap.R")
source("data_cleaning/04_carroll.R")
source("data_cleaning/05_cheshire.R")
source("data_cleaning/06_coos.R")
source("data_cleaning/07_grafton.R")
source("data_cleaning/08_hillsborough.R")
source("data_cleaning/09_merrimack.R")
source("data_cleaning/10_rockingham.R")
source("data_cleaning/11_strafford.R")
source("data_cleaning/12_sullivan.R")
```

## Belknap  

A - Asian  
B - Black   
C - Chinese  
H - Hispanic  
I - Indian  
NH - DELETE  
O - Other  
P - Portuguese  
U - Unknown  
W - White  
X - DELETE  
J - Japanese  

```{r}
view_df(belknap_adm_all)
```

## Carroll  

```{r}
view_df(carroll_adm_all)
```

## Cheshire  

A - Asian  
B - Black  
H - Hispanic  
I - Native American  
L - Latin / Hispanic  
P - Hawaiian or pacific islander  
U - Unknown  
W - White  

```{r}
view_df(cheshire_adm_all)
```

## Merrimack  

A - Asian  
B - Black or African American  
H - Hispanic or Latino  
I - American Indian or Alaskan  
P - Native Hawaiian or Other Pacific Islander  
U - Unknown  
W - White  
O - Unknown to data contact    
X - Unknown to data contact  

```{r}
view_df(merrimack_adm_all)
```

