---
title: "Data Dictionary"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  #dev = "ragg_png",
  cache = FALSE
  )
```

```{r include=FALSE}
# load data
load(paste0(sp_data_path, "/Data/r_data/belknap_adm_all.Rda",    sep = ""))
load(paste0(sp_data_path, "/Data/r_data/carroll_adm_all.Rda",    sep = ""))
load(paste0(sp_data_path, "/Data/r_data/cheshire_adm_all.Rda",   sep = ""))
load(paste0(sp_data_path, "/Data/r_data/coos_adm_all.Rda",       sep = ""))
load(paste0(sp_data_path, "/Data/r_data/merrimack_adm_all.Rda",  sep = ""))
load(paste0(sp_data_path, "/Data/r_data/rockingham_adm_all.Rda", sep = ""))
load(paste0(sp_data_path, "/Data/r_data/sullivan_adm_all.Rda",   sep = ""))
```

## Belknap  

A - Asian  
B - Black   
C - Chinese  
H - Hispanic  
I - Indian  
NH - DELETE  
O - Other  
P - Portuguese  
U - Unknown  
W - White  
X - DELETE  
J - Japanese  

```{r}
view_df(belknap_adm_all)
```

## Carroll  

```{r}
view_df(carroll_adm_all)
```

## Cheshire  

A - Asian  
B - Black  
H - Hispanic  
I - Native American  
L - Latin / Hispanic  
P - Hawaiian or pacific islander  
U - Unknown  
W - White  

```{r}
view_df(cheshire_adm_all)
```

## Coos

```{r}
view_df(coos_adm_all)
```

## Merrimack  

A - Asian  
B - Black or African American  
H - Hispanic or Latino  
I - American Indian or Alaskan  
P - Native Hawaiian or Other Pacific Islander  
U - Unknown  
W - White  
O - Unknown to data contact    
X - Unknown to data contact  

```{r}
view_df(merrimack_adm_all)
```

## Rockingham

```{r}
view_df(rockingham_adm_all)
```

## Sullivan

```{r}
view_df(sullivan_adm_all)
```
