---
title: "High Utilizers Trends"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  #dev = "ragg_png",
  cache = FALSE
  )

# load packages
source("data_cleaning/00_library.R")

# load data
load(paste0(sp_data_path, "/Data/r_data/hu_bookings_table.Rda", sep = ""))
load(paste0(sp_data_path, "/Data/r_data/hu_bookings_table_by_county.Rda", sep = ""))
```

# How we define High Utilizers

Using the jail administrative data submitted to CSG, we defined high utilizers as the top 1%, 3%, or 5% of people booked into jails each FY.



# Jail Bookings

## By Fiscal Year

The table below shows the number of HU bookings, proportion of HU bookings out of all bookings, and the average number of bookings per year for the three types of high utilizers for each FY and for all three years.  

```{r}
hu_bookings_table
```

## By County

The table below shows the number of HU bookings, proportion of HU bookings out of all bookings, and the average number of bookings per year for the three types of high utilizers for each county.

```{r}
hu_bookings_table_by_county
```


