---
title: "Incarceration Trends"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    theme: theme.css
    self_contained: false
---

The following incarceration patterns were found using jail administrative data submitted to DHHS, which was then de-identified and sent to CSG. This data gives a more accurate picture of the number of people entering NH jails from FY2019 to FY2021.  

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  dev = "ragg_png",
  cache = FALSE
  )

source("data_cleaning/00_library.R")
source("data_cleaning/01_functions.R")
source("data_cleaning/01_functions_visuals.R")
medicaid_jail_all <- read_rds("D:/Analytic/medicaid_jail_all.rds") 
```

# Entrances

**Includes**: People booked into jail for a criminal charge ("bookings") and protective custody (PC) holds. 
**Counties**: All New Hampshire counties except Grafton. Includes Coos bookings, but not their PC holds because Coos removed PC hold data from their system.   

### People Entered  

```{r, results='asis'}
```

<br>

### Number of Entrances  

Please Note: This section reflects the number of entrances per fiscal year, not the number of people.    

```{r, results='asis'}

```

```{r, out.width="50%", echo=FALSE, layout = "l-body"}
```

Counties saw variations in the number of entrances but they all saw a decrease in the past three years.

```{r}

```

**On average, people entered jails X times from 2019 to 2021.**

```{r}

```

<br>
<br>
