---
title: "Incarceration Patterns"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

The following incarceration patterns were found using jail administrative data submitted directly to CSG.   

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  #dev = "ragg_png",
  cache = FALSE
  )

source("data_cleaning/00_library.R")
source("data_cleaning/01_functions.R")
source("data_cleaning/01_functions_visuals.R")
source("data_cleaning/rdas.R")
```

# Bookings

**Includes**: People booked into jail for a criminal charge  
**Does Not Include**: PC holds  

**Counties**: All New Hampshire counties except Grafton and Strafford. Strafford is excluded because their data does not differentiate between bookings and PC holds.  

<br>

### People Booked By State

```{r, results='asis'}
# print header for pc hold section
cat("**There were ", amt_people_booked, " people booked into NH jails between FY2019 to FY2021.**\n\n", sep = "")
```
<br>

### Number of Bookings By State

Please Note: This section reflects the number of bookings per fiscal year, not the number of people.    

```{r, results='asis'}
# print header for pc hold section
cat("**There were ", amt_bookings, " bookings across New Hampshire from FY2019 to FY2021.**\n\n", sep = "")
```

```{r}
PRES_gg_bookings
```

```{r}
#row_bookings_fy
```

<br>

### Number of Bookings By County

Counties saw variations in the number of bookings but they all saw a decrease in the past three years.

```{r}
table_bookings_fy_county
```

<br>

# Booking Types

```{r}
#nh_booking_types
```

Coming soon. 

<br>

# Entrances

**Includes**: People booked into jail for a criminal charge ("bookings") and protective custody (PC) holds.  

**Counties**:

All New Hampshire counties except Grafton. Includes Coos bookings, but not PC holds.  
<br>

### People Entered By State

```{r, results='asis'}
# print header for pc hold section
cat("**There were ", amt_people_entered, " people who entered into NH jails between FY2019 to FY2021.**\n\n", sep = "")
```
<br>

### Number of Entrances By State

Please Note: This section reflects the number of entrances per fiscal year, not the number of people.    

```{r, results='asis'}
# print header for pc hold section
cat("**There were ", amt_entrances, " entrances across New Hampshire from FY2019 to FY2021 and an overall decrease of 38.1% since FY2019.**\n\n", sep = "")
```

```{r}
PRES_gg_entrances
```

```{r}
#row_entrances_fy
```

### Number of Entrances By County

Counties saw variations in the number of Entrances but they all saw a decrease in the past three years.

```{r}
PRES_table_entrances_fy_county
```

**On average, people entered jails 1.6 times from 2019 to 2021.**

```{r}
PRES_table_entrances_people_county
```

<br>

# Protective Custody Holds

### By State

```{r, results='asis'}
# print header for pc hold section
cat("**Protective custody holds accounted for ", amt_pch_pct, "% of bookings from 2019 to 2021.** Coos and Strafford are not included in this calculation due to missing data.\n\n", sep = "")
```
**Although the number of entrances has been decreasing, the proportion of PC holds has remained the same.**

```{r}
PRES_gg_pch_pct_barchart
```

<br>

**Protective custody holds tend to occur most frequently during summer months. There was a decline in protective custody holds at the start of the pandemic but they began climbing again shortly after.**  

```{r}
hc_pch_time
```

<br>

### By County

The proportion of entrances that were protective custody holds varied greatly by county. The table below shows the number of and proportion of entrances that included a protective custody hold charge. Belknap had the highest proportion of bookings that were protective custody holds.  

```{r}
PRES_table_entrances_with_pc_holds
```

<br>

**Some counties saw decreases in PC holds while others saw increases.**  

```{r}
table_pc_holds_fy_county
```

<br>

### How Protective Custody Holds Are Recorded

Each county records PC holds differently. PC holds are recorded in the charge description, booking type, sentence status, or release type, and sometimes across these metrics. See each **County Report** in the top menu to see how each county records PC holds and the "outcomes" of these holds.  

<br>
<br>
