---
title: "Medicaid Behavioral Health Encounters, Focusing on MH and SUD"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r include=FALSE}
# Load packages, functions, and data
source("data_cleaning/00_library.R")
source("data_cleaning/01_functions.R")
source("data_cleaning/rdas.R")

# Set chunk output 
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  dev = "ragg_png",
  cache = FALSE
  )
```

```{r include=FALSE}
# Load medicaid data
jail_medicaid_analytic_individual_booking_level <- read_rds("D:/Analytic/jail_medicaid_analytic_individual_booking_level.rds") 

# De-dup (there are a few duplicate bookings) and create booking id for analysis
jail_medicaid_analytic_individual_booking_level_dedup <- jail_medicaid_analytic_individual_booking_level %>% 
  distinct(unique_person_id, booking_id, .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(unique_person_id, booking_id)) 

# Recode high utilize percentile grouping, we don't need to group_by as the percentile grouping is already grouped across individual from Mari's cleaning
medicaid_individual_booking <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  
  # Recoded HU variable
  mutate(hu_group_exclusive = case_when(high_utilizer_10_pct =="No"     ~ 4,
                                        high_utilizer_10_pct =="Yes" & 
                                          high_utilizer_5_pct=="No" & 
                                          high_utilizer_1_pct=="No"     ~ 3,
                                        high_utilizer_5_pct  =="Yes" & 
                                          high_utilizer_1_pct=="No"     ~ 2,
                                        high_utilizer_1_pct  =="Yes"    ~ 1,
                                        TRUE ~ as.numeric(NA)),
         hu_group_exclusive = factor(hu_group_exclusive, 
                                     levels = c(1,2,3,4),
                                     labels = c("Top 1%", "Top 5%", "Top 10%", "Non-HU"))) %>% 
  # Overall HU variable
  mutate(hu_group_overall = case_when(high_utilizer_10_pct == "No"  ~ 2,
                                      high_utilizer_10_pct == "Yes" ~ 1,
                                      TRUE ~ as.numeric(NA)),
         hu_group_overall = factor(hu_group_overall,
                                   levels = c(1,2),
                                   labels = c("High Utilizer", "Non-High Utilizer")))
```         

# DHHS Medicaid Match and Jail Booking Descriptive Analysis: Behavioral Health Encounters by High Jail Utilizer Grouping

<br>

## Tables

### Table 1a: Mental Health and Substance Use Disorder Service Medicaid Encounters by **Overall** High Utilizer Grouping

Note: Co-Occurring Disorders indicates that individual had at least one Mental Health- and one Substance Use Disorder-related primary diagnoses in the Medicaid data.

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during the study period (Medicaid eligibility start date <= 6/30/2021). Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample")

```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_county_bh_service_type_hu_table <- medicaid_individual_booking %>% 
  dplyr::group_by(hu_group_overall) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ MH Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ SUD Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1 & pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (%)` = scales::percent(`Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_bh_mh_or_sud_service_secondary_dx_flag==1]),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (%)` = scales::percent(`Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Status` = hu_group_overall) 

# statewide
medicaid_jail_overall_bh_service_type_hu_table <- medicaid_individual_booking %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ MH Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ SUD Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                  
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1 & pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (%)` = scales::percent(`Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_bh_mh_or_sud_service_secondary_dx_flag==1]),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (%)` = scales::percent(`Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::mutate(`High Utilizer Status` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_county_statewide_bh_service_type_hu_table <- rbind(medicaid_jail_county_bh_service_type_hu_table,
                                                                 medicaid_jail_overall_bh_service_type_hu_table)

### print table via kableextra
kable(medicaid_jail_county_statewide_bh_service_type_hu_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  column_spec(12, bold = TRUE) %>% 
  scroll_box(width = "130%")
```

<br><br>

### Table 1b: Mental Health and Substance Use Disorder Service Medicaid Encounters by High Utilizer Grouping

Note: Co-Occurring Disorders indicates that individual had at least one Mental Health- and one Substance Use Disorder-related primary diagnoses in the Medicaid data.

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during  the study period (Medicaid eligibility start date <= 6/30/2021). Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample")

```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_county_bh_service_type_hu_table <- medicaid_individual_booking %>% 
  dplyr::group_by(hu_group_exclusive) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ MH Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ SUD Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1 & pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (%)` = scales::percent(`Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_bh_mh_or_sud_service_secondary_dx_flag==1]),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (%)` = scales::percent(`Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 

# statewide
medicaid_jail_overall_bh_service_type_hu_table <- medicaid_individual_booking %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ MH Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ SUD Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1 & pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (%)` = scales::percent(`Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_bh_mh_or_sud_service_secondary_dx_flag==1]),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (%)` = scales::percent(`Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::mutate(`High Utilizer Percentiles` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_county_statewide_bh_service_type_hu_table <- rbind(medicaid_jail_county_bh_service_type_hu_table,
                                                                 medicaid_jail_overall_bh_service_type_hu_table)

### print table via kableextra
kable(medicaid_jail_county_statewide_bh_service_type_hu_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  column_spec(12, bold = TRUE) %>% 
  scroll_box(width = "130%")

```

<br><br>

### Table 2a: Percentage of Individuals with SMI or Opioid-related Primary Diagnoses (Individual-level) by **Overall** High Utilizer Grouping

**Update**: Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample"). I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during the study period. The following primary diagnoses are coded as "SMI" -- based on National Alliance on Mental Illness New Hampshire's definition (NAMI NH), which David shared:

*	Schizophrenia (dx_prmry_clinical_classification = "Schizophrenia and other psychotic disorders", "Schizophrenia spectrum and other psychotic disorders")

*	Bipolar Disorder (dx_prmry_clinical_classification = "Bipolar and related disorders")

*	Major Depression (dx_prmry_clinical_classification = "Depressive disorders")

*	Post-Traumatic Stress Disorder (dx_prmry_clinical_classification = "Trauma- and stressor-related disorders")

*	Borderline Personality Disorder (dx_prmry_clinical_classification = "Personality disorders")

*	Obsessive-Compulsive Disorder (dx_prmry_clinical_classification = "Obsessive-compulsive and related disorders", "Disruptive, impulse-control and conduct disorder")

*	Panic Disorder (nothing coded)

*	Phobias (nothing coded)

*	Eating Disorders (nothing coded)

*	I also included the following diagnoses because it seems like they fit within the definition: dx_prmry_clinical_classification = "Mood disorders" or "Other specified and unspecified mood disorders"


```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_smi_opioid_hu_grouping <- medicaid_individual_booking %>% 
  dplyr::group_by(hu_group_overall) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ SMI Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_smi_flag==1]),
                   `Individuals w/ SMI Primary Diagnosis (%)` = scales::percent(`Individuals w/ SMI Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ Opioid-related Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_opioid_related_flag==1]),
                   `Individuals w/ Opioid-related Primary Diagnosis (%)` = scales::percent(`Individuals w/ Opioid-related Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`)) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Status` = hu_group_overall) 

# statewide
medicaid_jail_smi_opioid_statewide <- medicaid_individual_booking %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ SMI Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_smi_flag==1]),
                   `Individuals w/ SMI Primary Diagnosis (%)` = scales::percent(`Individuals w/ SMI Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ Opioid-related Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_opioid_related_flag==1]),
                   `Individuals w/ Opioid-related Primary Diagnosis (%)` = scales::percent(`Individuals w/ Opioid-related Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`)) %>% 
  dplyr::mutate(`High Utilizer Status` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_smi_opioid_hu_grouping_statewide_table <- rbind(medicaid_jail_smi_opioid_hu_grouping,
                                                               medicaid_jail_smi_opioid_statewide)

### print table via kableextra
kable(medicaid_jail_smi_opioid_hu_grouping_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  scroll_box(width = "130%")

```

<br><br>

### Table 2b: Percentage of Individuals with SMI or Opioid-related Primary Diagnoses (Individual-level)

**Update**: Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample"). I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during the study period. The following primary diagnoses are coded as "SMI" -- based on National Alliance on Mental Illness New Hampshire's definition (NAMI NH), which David shared:

*	Schizophrenia (dx_prmry_clinical_classification = "Schizophrenia and other psychotic disorders", "Schizophrenia spectrum and other psychotic disorders")

*	Bipolar Disorder (dx_prmry_clinical_classification = "Bipolar and related disorders")

*	Major Depression (dx_prmry_clinical_classification = "Depressive disorders")

*	Post-Traumatic Stress Disorder (dx_prmry_clinical_classification = "Trauma- and stressor-related disorders")

*	Borderline Personality Disorder (dx_prmry_clinical_classification = "Personality disorders")

*	Obsessive-Compulsive Disorder (dx_prmry_clinical_classification = "Obsessive-compulsive and related disorders", "Disruptive, impulse-control and conduct disorder")

*	Panic Disorder (nothing coded)

*	Phobias (nothing coded)

*	Eating Disorders (nothing coded)

*	I also included the following diagnoses because it seems like they fit within the definition: dx_prmry_clinical_classification = "Mood disorders" or "Other specified and unspecified mood disorders"

```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_smi_opioid_hu_grouping <- medicaid_individual_booking %>% 
  dplyr::group_by(hu_group_exclusive) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ SMI Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_smi_flag==1]),
                   `Individuals w/ SMI Primary Diagnosis (%)` = scales::percent(`Individuals w/ SMI Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ Opioid-related Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_opioid_related_flag==1]),
                   `Individuals w/ Opioid-related Primary Diagnosis (%)` = scales::percent(`Individuals w/ Opioid-related Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`)) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 

# statewide
medicaid_jail_smi_opioid_statewide <- medicaid_individual_booking %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ SMI Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_smi_flag==1]),
                   `Individuals w/ SMI Primary Diagnosis (%)` = scales::percent(`Individuals w/ SMI Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ Opioid-related Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_opioid_related_flag==1]),
                   `Individuals w/ Opioid-related Primary Diagnosis (%)` = scales::percent(`Individuals w/ Opioid-related Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`)) %>% 
  dplyr::mutate(`High Utilizer Percentiles` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_smi_opioid_hu_grouping_statewide_table <- rbind(medicaid_jail_smi_opioid_hu_grouping,
                                                               medicaid_jail_smi_opioid_statewide)

### print table via kableextra
kable(medicaid_jail_smi_opioid_hu_grouping_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  scroll_box(width = "130%")

```

<br><br>

**See full notes and business rules for variable creation in data dictionary for individual-level analytic file here: https://csgorg.sharepoint.com/:x:/s/Team-JC-Research/EUJfEABIuNNBvKARa4Kq1nwBvSLwsK4aH7K9oZDOWxbc1w?e=zLytTB**

<br><br>
