---
title: "Medicaid Behavioral Health Encounters, Focusing on CMHC and ED Visits, Pharmacy Visits"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r include=FALSE}
# Load packages, functions, and data
source("data_cleaning/00_library.R")
source("data_cleaning/01_functions.R")
source("data_cleaning/rdas.R")

### set path for viz output (andrew's viz folder)
sp_viz_output_path <- csg_sp_path(file.path("JR_NH/Output/r_output_presentation"))

### set chunk output 
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  dev = "ragg_png",
  cache = FALSE
  )
```

```{r include=FALSE}
### import adm_all -- jail administrative that we'll compare to the numbers from the medicaid match files
load(paste0(sp_data_path, "/Data/r_data/adm_all.Rda", 
            sep = "")) 

### de-dup by individual and booking -- these are the two units of analysis for comparisons to the medicaid data
### here we are de-duping bookings with multiple charges as we don't need that information for this comparison
adm_all_dedup <- adm_all %>% 
  ungroup() %>% 
  distinct(id, 
           booking_id,
           .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(id,
                                    booking_id)) ### creating unique booking id with both individual and booking IDs


### import medicaid_jail_all -- medicaid jail data that we'll compare to the numbers from the jail administrative files
### this file lives on the external hard drive (created and exported in `14_medicaid.R`)
medicaid_jail_all <- read_rds("D:/Analytic/medicaid_jail_all.rds") 

### de-dup (there are a few duplicate bookings) and create booking id for analysis
medicaid_jail_all_dedup <- medicaid_jail_all %>% 
  distinct(unique_person_id, 
           booking_id,
           .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(unique_person_id,
                                    booking_id)) ### creating unique booking id with both individual and booking IDs

### import jail_medicaid_analytic_individual_booking_level -- the individual-level analytic file created with all DHHS files
### file is unique by individual/booking
### this file lives on the external hard drive (created and exported in `14_medicaid.R`)
jail_medicaid_analytic_individual_booking_level <- read_rds("D:/Analytic/jail_medicaid_analytic_individual_booking_level.rds") 

### de-dup (there are a few duplicate bookings) and create booking id for analysis
jail_medicaid_analytic_individual_booking_level_dedup <- jail_medicaid_analytic_individual_booking_level %>% 
  distinct(unique_person_id, 
           booking_id,
           .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(unique_person_id,
                                    booking_id)) ### creating unique booking id with both individual and booking IDs

### to recode high utlizer percentile grouping, we don't need to group_by as the percentile grouping is already grouped across individual from Mari's cleaning
jail_medicaid_analytic_individual_booking_level_dedup_hu_recode <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  ### to ensure each individual/booking is in correct grouping, start with Non-HU, then 10% and move down to 1%
  mutate(hu_group_exclusive = case_when(
    high_utilizer_10_pct=="No" ~ 4,
    high_utilizer_10_pct=="Yes" & high_utilizer_5_pct=="No" & high_utilizer_1_pct=="No" ~ 3,
    high_utilizer_5_pct=="Yes" & high_utilizer_1_pct=="No" ~ 2,
    high_utilizer_1_pct=="Yes" ~ 1,
    TRUE ~ as.numeric(NA)),
    hu_group_exclusive = factor(hu_group_exclusive,
         levels = c(1,2,3,4),
         labels = c("Tier 1 HU", "Tier 2 HU", "Tier 3 HU", "Non-HU"))) %>% 
  ### now create overall hu grouping -- either yes or no
  mutate(hu_group_overall = case_when(
    high_utilizer_10_pct=="No" ~ 2,
    high_utilizer_10_pct=="Yes" ~ 1,
    TRUE ~ as.numeric(NA)),
    hu_group_overall = factor(hu_group_overall,
         levels = c(1,2),
         labels = c("High Utilizer", "Non-High Utilizer")))

### read in and merge cdc_county_rural_urban_crosswalk: https://www.cdc.gov/nchs/data_access/urban_rural.htm
cdc_county_rural_urban_crosswalk <- openxlsx::read.xlsx(file.path(sp_data_path,"Data/US County Geo Data/CDC_NCHSURCodes2013.xlsx"), 
                                                        sheet = "NCHSURCodes2013") %>%
  clean_names() %>%
  dplyr::filter(state_abr == "NH") %>%
  mutate(cdc_urban_rural_classification = case_when(
    x2013_code=="1" ~ "Urban Center",
    x2013_code=="2" ~ "Suburb",
    x2013_code=="3" ~ "Medium City",
    x2013_code=="4" ~ "Small City",
    x2013_code=="5" ~ "Town", 
    x2013_code=="6" ~ "Rural Area",### see: https://www.cdc.gov/nchs/data/data_acces_files/NCHSUrbruralFileDocumentationInternet2.pd
# from matt:
# Large central metro > Urban centers
# Large fringe metro > Suburbs
# Medium metro > Medium cities
# Small metro > Small cities
# Micropolitan > Towns
# Non-core > Rural areas
    TRUE ~ as.character(NA))) %>% 
  dplyr::select(county_name,cdc_urban_rural_classification) %>% 
  mutate(county = str_remove(county_name,
                             pattern = " County"))

### join cdc_county_rural_urban_crosswalk to jail_medicaid_analytic_individual_booking_level_dedup_hu_recode
jail_medicaid_analytic_individual_booking_level_dedup_hu_recode_cdc <- left_join(jail_medicaid_analytic_individual_booking_level_dedup_hu_recode,
                                                  cdc_county_rural_urban_crosswalk,
                                                  by = "county") 
```         

# DHHS Medicaid Match and Jail Booking Descriptive Analysis: Behavioral Health Encounters by High Jail Utilizer Grouping

<br>

## Tables

### Table 1a: Mental Health and Substance Use Disorder Service Medicaid Encounters by **Overall** High Utilizer Grouping

Note: Co-Occurring Disorders indicates that individual had at least one Mental Health- and one Substance Use Disorder-related primary diagnoses in the Medicaid data.

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during  the study period (Medicaid eligibility start date <= 6/30/2021). Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample")

```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_county_bh_service_type_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(hu_group_overall) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ MH Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ SUD Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1 & pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (%)` = scales::percent(`Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_bh_mh_or_sud_service_secondary_dx_flag==1]),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (%)` = scales::percent(`Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Status` = hu_group_overall) 

# statewide
medicaid_jail_overall_bh_service_type_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ MH Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ SUD Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1 & pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (%)` = scales::percent(`Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_bh_mh_or_sud_service_secondary_dx_flag==1]),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (%)` = scales::percent(`Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::mutate(`High Utilizer Status` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_county_statewide_bh_service_type_hu_table <- rbind(medicaid_jail_county_bh_service_type_hu_table,
                                                                 medicaid_jail_overall_bh_service_type_hu_table)

### print table via kableextra
kable(medicaid_jail_county_statewide_bh_service_type_hu_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  column_spec(12, bold = TRUE) %>% 
  scroll_box(width = "130%")

```

<br><br>

### Table 1b: Mental Health and Substance Use Disorder Service Medicaid Encounters by High Utilizer Grouping

Note: Co-Occurring Disorders indicates that individual had at least one Mental Health- and one Substance Use Disorder-related primary diagnoses in the Medicaid data.

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during  the study period (Medicaid eligibility start date <= 6/30/2021). Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample")

```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_county_bh_service_type_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(hu_group_exclusive) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ MH Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ SUD Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1 & pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (%)` = scales::percent(`Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_bh_mh_or_sud_service_secondary_dx_flag==1]),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (%)` = scales::percent(`Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 

# statewide
medicaid_jail_overall_bh_service_type_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ MH Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ MH Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ SUD Service Encounter, Primary Diagnosis (%)` = scales::percent(`Individuals w/ SUD Service Encounter, Primary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1 & pre_or_study_sud_service_primary_dx_flag==1]),
                   `Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (%)` = scales::percent(`Individuals w/ MH and SUD Service Encounters, Co-Occurring Disorders (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_bh_mh_or_sud_service_secondary_dx_flag==1]),
                   `Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (%)` = scales::percent(`Individuals w/ MH or SUD Service Encounter, Secondary Diagnosis (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::mutate(`High Utilizer Percentiles` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_county_statewide_bh_service_type_hu_table <- rbind(medicaid_jail_county_bh_service_type_hu_table,
                                                                 medicaid_jail_overall_bh_service_type_hu_table)

### print table via kableextra
kable(medicaid_jail_county_statewide_bh_service_type_hu_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  column_spec(12, bold = TRUE) %>% 
  scroll_box(width = "130%")

```

<br><br>

### Table 2a: CMHC and ED Visits by **Overall** High Utilizer Grouping

Note: Need to think through substantial difference between mean and median ED visits and how to talk through each metric if we end up presenting them. Related to this, there seem to be a handful of outliers (e.g., 100+ ED visits) that I need to further explore. 

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during  the study period. Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample")

```{r echo=FALSE,message=FALSE,warning=FALSE} 
### need to recode count of ED services from NA to 0 when pre_or_study_window_medicaid_match_flag_overall==1 before we calculate the mean
### NA values now indicate that individual didn't match to medicaid data whereas 0 indicates that individual did
### match to medicaid data, but had no recorded BH-related ED visits
### also need to de-dup file by individual before taking mean -- so that we have one ED visit count per individual, not
### per booking
jail_medicaid_analytic_individual_booking_level_dedup_ed_visit_count_recode <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  mutate(pre_or_study_ed_visit_or_service_encounter_count = ifelse(is.na(pre_or_study_ed_visit_or_service_encounter_count)==TRUE & pre_or_study_window_medicaid_match_flag_overall==1,
                                                            0,pre_or_study_ed_visit_or_service_encounter_count)) %>% 
  distinct(unique_person_id,
           .keep_all=TRUE)

# by hu_group_exclusive
medicaid_jail_ed_visits_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_ed_visit_count_recode %>% 
  dplyr::group_by(hu_group_overall) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Service provided by CMHC (N)` = n_distinct(unique_person_id[pre_or_study_service_provided_by_cmhc_provider_flag==1]),
                   `Individuals w/ BH Service provided by CMHC (%)` = scales::percent(`Individuals w/ BH Service provided by CMHC (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ BH Service provided by ED (N)` = n_distinct(unique_person_id[pre_or_study_ed_visit_or_service_flag==1]),
                   `Individuals w/ BH Service provided by ED (%)` = scales::percent(`Individuals w/ BH Service provided by ED (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Total Encounters w/ BH Service provided by ED (N)` = sum(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_service_provided_by_cmhc_provider_flag==1],
                                                                               na.rm = TRUE),
                   `Mean ED visits for BH Service per Individual (Medicaid match sample)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (Medicaid match sample)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (BH encounter sample mean)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (BH encounter sample mean)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1)) %>%
  ungroup() %>% 
  dplyr::rename(`High Utilizer Status` = hu_group_overall) 

# statewide
medicaid_jail_ed_visits_hu_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup_ed_visit_count_recode %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Service provided by CMHC (N)` = n_distinct(unique_person_id[pre_or_study_service_provided_by_cmhc_provider_flag==1]),
                   `Individuals w/ BH Service provided by CMHC (%)` = scales::percent(`Individuals w/ BH Service provided by CMHC (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ BH Service provided by ED (N)` = n_distinct(unique_person_id[pre_or_study_ed_visit_or_service_flag==1]),
                   `Individuals w/ BH Service provided by ED (%)` = scales::percent(`Individuals w/ BH Service provided by ED (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Total Encounters w/ BH Service provided by ED (N)` = sum(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_service_provided_by_cmhc_provider_flag==1],
                                                                               na.rm = TRUE),
                   `Mean ED visits for BH Service per Individual (Medicaid match sample)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (Medicaid match sample)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (BH encounter sample mean)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (BH encounter sample mean)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1)) %>%
  dplyr::mutate(`High Utilizer Status` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_ed_visits_hu_overall_table <- rbind(medicaid_jail_ed_visits_hu_table,
                                                  medicaid_jail_ed_visits_hu_overall_table)

### print table via kableextra
kable(medicaid_jail_ed_visits_hu_overall_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE) %>% 
  column_spec(5, bold = TRUE) %>% 
  column_spec(7, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(9, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  column_spec(11, bold = TRUE) %>% 
  column_spec(12, bold = TRUE) %>% 
  column_spec(13, bold = TRUE) %>% 
  scroll_box(width = "130%")
```

<br><br>

### Table 2b: CMHC and ED Visits by High Utilizer Grouping

Note: Need to think through substantial difference between mean and median ED visits and how to talk through each metric if we end up presenting them. Related to this, there seem to be a handful of outliers (e.g., 100+ ED visits) that I need to further explore. 

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during  the study period. Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample")

```{r echo=FALSE,message=FALSE,warning=FALSE} 
### need to recode count of ED services from NA to 0 when pre_or_study_window_medicaid_match_flag_overall==1 before we calculate the mean
### NA values now indicate that individual didn't match to medicaid data whereas 0 indicates that individual did
### match to medicaid data, but had no recorded BH-related ED visits
### also need to de-dup file by individual before taking mean -- so that we have one ED visit count per individual, not
### per booking
jail_medicaid_analytic_individual_booking_level_dedup_ed_visit_count_recode <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  mutate(pre_or_study_ed_visit_or_service_encounter_count = ifelse(is.na(pre_or_study_ed_visit_or_service_encounter_count)==TRUE & pre_or_study_window_medicaid_match_flag_overall==1,
                                                            0,pre_or_study_ed_visit_or_service_encounter_count)) %>% 
  distinct(unique_person_id,
           .keep_all=TRUE)

# by hu_group_exclusive
medicaid_jail_ed_visits_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_ed_visit_count_recode %>% 
  dplyr::group_by(hu_group_exclusive) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Service provided by CMHC (N)` = n_distinct(unique_person_id[pre_or_study_service_provided_by_cmhc_provider_flag==1]),
                   `Individuals w/ BH Service provided by CMHC (%)` = scales::percent(`Individuals w/ BH Service provided by CMHC (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ BH Service provided by ED (N)` = n_distinct(unique_person_id[pre_or_study_ed_visit_or_service_flag==1]),
                   `Individuals w/ BH Service provided by ED (%)` = scales::percent(`Individuals w/ BH Service provided by ED (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Total Encounters w/ BH Service provided by ED (N)` = sum(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_service_provided_by_cmhc_provider_flag==1],
                                                                               na.rm = TRUE),
                   `Mean ED visits for BH Service per Individual (Medicaid match sample)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (Medicaid match sample)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (BH encounter sample mean)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (BH encounter sample mean)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1)) %>%
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 

# statewide
medicaid_jail_ed_visits_hu_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup_ed_visit_count_recode %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Service provided by CMHC (N)` = n_distinct(unique_person_id[pre_or_study_service_provided_by_cmhc_provider_flag==1]),
                   `Individuals w/ BH Service provided by CMHC (%)` = scales::percent(`Individuals w/ BH Service provided by CMHC (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ BH Service provided by ED (N)` = n_distinct(unique_person_id[pre_or_study_ed_visit_or_service_flag==1]),
                   `Individuals w/ BH Service provided by ED (%)` = scales::percent(`Individuals w/ BH Service provided by ED (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Total Encounters w/ BH Service provided by ED (N)` = sum(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_service_provided_by_cmhc_provider_flag==1],
                                                                               na.rm = TRUE),
                   `Mean ED visits for BH Service per Individual (Medicaid match sample)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (Medicaid match sample)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (BH encounter sample mean)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (BH encounter sample mean)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1)) %>%
  dplyr::mutate(`High Utilizer Percentiles` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_ed_visits_hu_overall_table <- rbind(medicaid_jail_ed_visits_hu_table,
                                                  medicaid_jail_ed_visits_hu_overall_table)

### print table via kableextra
kable(medicaid_jail_ed_visits_hu_overall_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE) %>% 
  column_spec(5, bold = TRUE) %>% 
  column_spec(7, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(9, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  column_spec(11, bold = TRUE) %>% 
  column_spec(12, bold = TRUE) %>% 
  column_spec(13, bold = TRUE) %>% 
  scroll_box(width = "130%")
```

<br><br>

### Figure 1. ED and CMHC Visits by HU Grouping

```{r layout="l-body-outset",echo=FALSE,message=FALSE,warning=FALSE}
# by hu_group_exclusive
medicaid_jail_ed_visits_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_ed_visit_count_recode %>% 
  dplyr::group_by(hu_group_exclusive) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Service provided by CMHC (N)` = n_distinct(unique_person_id[pre_or_study_service_provided_by_cmhc_provider_flag==1]),
                   `Individuals w/ BH Service provided by CMHC (%)` = `Individuals w/ BH Service provided by CMHC (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ BH Service provided by ED (N)` = n_distinct(unique_person_id[pre_or_study_ed_visit_or_service_flag==1]),
                   `Individuals w/ BH Service provided by ED (%)` = `Individuals w/ BH Service provided by ED (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Total Encounters w/ BH Service provided by ED (N)` = sum(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_service_provided_by_cmhc_provider_flag==1],
                                                                               na.rm = TRUE),
                   `Mean ED visits for BH Service per Individual (Medicaid match sample)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (Medicaid match sample)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_window_medicaid_match_flag_overall==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (BH encounter sample mean)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (BH encounter sample mean)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_bh_flag==1], na.rm = TRUE), digits = 1),
                   `Mean ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(mean(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1),
                   `Median ED visits for BH Service per Individual (mean for those w/ 1+ ED visit)` = round(median(pre_or_study_ed_visit_or_service_encounter_count[pre_or_study_ed_visit_or_service_flag==1], na.rm = TRUE), digits = 1)) %>%
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 

### prep both dataframes for ggplot
medicaid_jail_ed_visits_hu_overall_table_to_viz <- medicaid_jail_ed_visits_hu_table %>% 
  dplyr::select(`High Utilizer Percentiles`,
                `Individuals w/ BH Service provided by CMHC (%)`,
                `Individuals w/ BH Service provided by ED (%)`)

### pivot wide to long for geom_bar
medicaid_jail_ed_visits_hu_overall_table_bar <- medicaid_jail_ed_visits_hu_overall_table_to_viz %>%
  dplyr::select(`High Utilizer Percentiles`,`Individuals w/ BH Service provided by CMHC (%)`,`Individuals w/ BH Service provided by ED (%)`) %>%
  gather(`sample_state`, percentage, `Individuals w/ BH Service provided by CMHC (%)`:`Individuals w/ BH Service provided by ED (%)`) %>% 
  mutate(`sample_state` = case_when(`sample_state`=="Individuals w/ BH Service provided by CMHC (%)"~"Community Mental\nHealth Center\n(CMHC)",
                                    `sample_state`=="Individuals w/ BH Service provided by ED (%)"~"Emergency Department\n(ED)",
         TRUE ~ as.character(NA))) %>% 
  mutate(`sample_state` = factor(`sample_state`,
                                levels = c("Community Mental\nHealth Center\n(CMHC)","Emergency Department\n(ED)"))) 

### plot
ggplot(data = medicaid_jail_ed_visits_hu_overall_table_bar, aes(y = percentage, x = forcats::fct_rev(`High Utilizer Percentiles`), fill = sample_state)) + 
  geom_bar(stat = "identity", position = "dodge", color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.8))) +
  scale_fill_manual(values = c("#167a9c","#293e5c")) +
  scale_color_manual(values = c("#167a9c","#293e5c")) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
 theme(legend.position = "top",
        legend.title.align=0.5,
       axis.text.x = element_text(size = 10.5, face="bold"),
       axis.ticks.length = unit(0, "cm"),
       plot.caption = element_text(hjust = 0.5),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11.5,
                              margin=margin(r=10)),
               # panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  # coord_flip() + 
  # facet_grid(`Gender` ~ ., scales="free_y", space="free_y", switch="y") +
 guides(fill = guide_legend(reverse = FALSE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
  geom_label_repel(aes(label = scales::percent(as.numeric(percentage),
                                               accuracy = 0.1),
                   color = sample_state),
                   position = position_dodge(.9),
                  # direction = 'y',
                  vjust = .65,
                  hjust = .5,               
                   fill = "white",
                   label.padding = 0.2,
                   box.padding = 0.2,
                   size = 4.75,
                   segment.color = NA,
                   fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "ed_cmhc_visits_percent_by_hu.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br><br>

### Figure 2. SMI- and Opioid-related ED Visits by HU Grouping

```{r layout="l-body-outset",echo=FALSE,message=FALSE,warning=FALSE}
# medicaid_enrollment_categories_encounters_individual_jail_all <- read_rds("D:/Analytic/jail_medicaid_analytic_individual_booking_level_pre_study_only.rds") %>% 
#    ### to ensure each individual/booking is in correct grouping, start with Non-HU, then 10% and move down to 1%
#   mutate(hu_group_exclusive = case_when(
#     high_utilizer_10_pct=="No" ~ 4,
#     high_utilizer_10_pct=="Yes" & high_utilizer_5_pct=="No" & high_utilizer_1_pct=="No" ~ 3,
#     high_utilizer_5_pct=="Yes" & high_utilizer_1_pct=="No" ~ 2,
#     high_utilizer_1_pct=="Yes" ~ 1,
#     TRUE ~ as.numeric(NA)),
#     hu_group_exclusive = factor(hu_group_exclusive,
#          levels = c(1,2,3,4),
#          labels = c("Tier 1 HU", "Tier 2 HU", "Tier 3 HU", "Non-HU"))) %>% 
#   ### now create overall hu grouping -- either yes or no
#   mutate(hu_group_overall = case_when(
#     high_utilizer_10_pct=="No" ~ 2,
#     high_utilizer_10_pct=="Yes" ~ 1,
#     TRUE ~ as.numeric(NA)),
#     hu_group_overall = factor(hu_group_overall,
#          levels = c(1,2),
#          labels = c("High Utilizer", "Non-High Utilizer")))

# by hu_group_exclusive
medicaid_jail_ed_smi_opioid_visits_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(hu_group_exclusive) %>%
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `ED and SMI Visits (N)` = n_distinct(unique_person_id[pre_or_study_ed_visit_or_service_related_to_smi_flag==1]),
                   `ED and SMI Visits (%)` = `ED and SMI Visits (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `ED and Opioid Visits (N)` = n_distinct(unique_person_id[pre_or_study_ed_visit_or_service_related_to_opioid_flag==1]),
                   `ED and Opioid Visits (%)` = `ED and Opioid Visits (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])) %>%
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 


### prep both dataframes for ggplot
medicaid_jail_ed_smi_opioid_visits_hu_table_to_viz <- medicaid_jail_ed_smi_opioid_visits_hu_table %>% 
  dplyr::select(`High Utilizer Percentiles`,
                `ED and SMI Visits (%)`,
                `ED and Opioid Visits (%)`)

### pivot wide to long for geom_bar
medicaid_jail_ed_smi_opioid_visits_hu_table_bar <- medicaid_jail_ed_smi_opioid_visits_hu_table_to_viz %>%
  dplyr::select(`High Utilizer Percentiles`,`ED and SMI Visits (%)`,`ED and Opioid Visits (%)`) %>%
  gather(`sample_state`, percentage, `ED and SMI Visits (%)`:`ED and Opioid Visits (%)`) %>% 
  mutate(`sample_state` = case_when(`sample_state`=="ED and SMI Visits (%)"~"SMI-related ED Visits",
                                    `sample_state`=="ED and Opioid Visits (%)"~"Opioid-related ED Visits",
         TRUE ~ as.character(NA))) %>% 
  mutate(`sample_state` = factor(`sample_state`,
                                levels = c("SMI-related ED Visits","Opioid-related ED Visits"))) 

### plot
ggplot(data = medicaid_jail_ed_smi_opioid_visits_hu_table_bar, aes(y = percentage, x = forcats::fct_rev(`High Utilizer Percentiles`), fill = sample_state)) + 
  geom_bar(stat = "identity", position = "dodge", color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1),
                     limits=c(min(0), 
                                           max(.4))) +
  scale_fill_manual(values = c("#167a9c","#293e5c")) +
  scale_color_manual(values = c("#167a9c","#293e5c")) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
 theme(legend.position = "top",
        legend.title.align=0.5,
       axis.text.x = element_text(size = 10.5, face="bold"),
       axis.ticks.length = unit(0, "cm"),
       plot.caption = element_text(hjust = 0.5),
        strip.placement="outside",
        strip.text.x=element_text(angle=180, hjust=1, face="bold", size=11.5,
                              margin=margin(r=10)),
               # panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  # coord_flip() + 
  # facet_grid(`Gender` ~ ., scales="free_y", space="free_y", switch="y") +
 guides(fill = guide_legend(reverse = FALSE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
  geom_label_repel(aes(label = scales::percent(as.numeric(percentage),
                                               accuracy = 0.1),
                   color = sample_state),
                   position = position_dodge(.9),
                  # direction = 'y',
                  vjust = .65,
                  hjust = .5,               
                   fill = "white",
                   label.padding = 0.1,
                   box.padding = 0.1,
                   size = 4.75,
                   segment.color = NA,
                   fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "smi_opioid_related_ed_visits_percent_by_hu.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br><br>

### Table 3a: Pharmacy Visits and Other Behavioral Health Services by **Overall** High Utilizer Grouping

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during  the study period. Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample")

```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_county_pharmacy_type_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(hu_group_overall) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                    `Individuals w/ MH Pharmacy Service (N)` = n_distinct(unique_person_id[pre_or_study_mental_health_pharmacy_service_flag==1]),
                   `Individuals w/ MH Pharmacy Service (%)` = scales::percent(`Individuals w/ MH Pharmacy Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Pharmacy Service (N)` = n_distinct(unique_person_id[pre_or_study_sud_pharmacy_service_flag==1]),
                   `Individuals w/ SUD Pharmacy Service (%)` = scales::percent(`Individuals w/ SUD Pharmacy Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ Other BH Service (N)` = n_distinct(unique_person_id[pre_or_study_other_service_flag==1]),
                   `Individuals w/ Other BH Service (%)` = scales::percent(`Individuals w/ Other BH Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Status` = hu_group_overall) 

# statewide
medicaid_jail_county_pharmacy_type_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                    `Individuals w/ MH Pharmacy Service (N)` = n_distinct(unique_person_id[pre_or_study_mental_health_pharmacy_service_flag==1]),
                   `Individuals w/ MH Pharmacy Service (%)` = scales::percent(`Individuals w/ MH Pharmacy Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Pharmacy Service (N)` = n_distinct(unique_person_id[pre_or_study_sud_pharmacy_service_flag==1]),
                   `Individuals w/ SUD Pharmacy Service (%)` = scales::percent(`Individuals w/ SUD Pharmacy Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ Other BH Service (N)` = n_distinct(unique_person_id[pre_or_study_other_service_flag==1]),
                   `Individuals w/ Other BH Service (%)` = scales::percent(`Individuals w/ Other BH Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  dplyr::mutate(`High Utilizer Status` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_county_statewide_pharmacy_type_hu_table <- rbind(medicaid_jail_county_pharmacy_type_hu_table,
                                                               medicaid_jail_county_pharmacy_type_overall_table)

### print table via kableextra
kable(medicaid_jail_county_statewide_pharmacy_type_hu_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  scroll_box(width = "130%")

```

<br><br>

### Table 3b: Pharmacy Visits and Other Behavioral Health Services by High Utilizer Grouping

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during  the study period. Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample")

```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_county_pharmacy_type_hu_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(hu_group_exclusive) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                    `Individuals w/ MH Pharmacy Service (N)` = n_distinct(unique_person_id[pre_or_study_mental_health_pharmacy_service_flag==1]),
                   `Individuals w/ MH Pharmacy Service (%)` = scales::percent(`Individuals w/ MH Pharmacy Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Pharmacy Service (N)` = n_distinct(unique_person_id[pre_or_study_sud_pharmacy_service_flag==1]),
                   `Individuals w/ SUD Pharmacy Service (%)` = scales::percent(`Individuals w/ SUD Pharmacy Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ Other BH Service (N)` = n_distinct(unique_person_id[pre_or_study_other_service_flag==1]),
                   `Individuals w/ Other BH Service (%)` = scales::percent(`Individuals w/ Other BH Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 

# statewide
medicaid_jail_county_pharmacy_type_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (%)` = scales::percent(n_distinct(unique_person_id[pre_or_study_bh_flag==1])/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                    `Individuals w/ MH Pharmacy Service (N)` = n_distinct(unique_person_id[pre_or_study_mental_health_pharmacy_service_flag==1]),
                   `Individuals w/ MH Pharmacy Service (%)` = scales::percent(`Individuals w/ MH Pharmacy Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ SUD Pharmacy Service (N)` = n_distinct(unique_person_id[pre_or_study_sud_pharmacy_service_flag==1]),
                   `Individuals w/ SUD Pharmacy Service (%)` = scales::percent(`Individuals w/ SUD Pharmacy Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1])),
                   `Individuals w/ Other BH Service (N)` = n_distinct(unique_person_id[pre_or_study_other_service_flag==1]),
                   `Individuals w/ Other BH Service (%)` = scales::percent(`Individuals w/ Other BH Service (N)`/n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]))) %>% 
  dplyr::mutate(`High Utilizer Percentiles` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_county_statewide_pharmacy_type_hu_table <- rbind(medicaid_jail_county_pharmacy_type_hu_table,
                                                               medicaid_jail_county_pharmacy_type_overall_table)

### print table via kableextra
kable(medicaid_jail_county_statewide_pharmacy_type_hu_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  scroll_box(width = "130%")

```

<br><br>

### Table 4a: Percentage of Individuals with SMI or Opioid-related Primary Diagnoses (Individual-level) by **Overall** High Utilizer Grouping

This table explores the percentage of individuals in the sample with SMI or Opioid-related primary diagnoses, based on the following slides in the powerpoint: 

* Slide 38: A closer look at serious SMI's (bipolar disorder, schizophrenia, etc.) 

* Slide 40: HU's ____% more likely to have an opioid use disorder

**See full notes and business rules for variable creation in data dictionary for individual-level analytic file here: https://csgorg.sharepoint.com/:x:/s/Team-JC-Research/EUJfEABIuNNBvKARa4Kq1nwBvSLwsK4aH7K9oZDOWxbc1w?e=zLytTB**


**Update**: Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample"). I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during the study period. The following primary diagnoses are coded as "SMI" -- based on National Alliance on Mental Illness New Hampshire's definition (NAMI NH), which David shared:

*	Schizophrenia (dx_prmry_clinical_classification = "Schizophrenia and other psychotic disorders", "Schizophrenia spectrum and other psychotic disorders")

*	Bipolar Disorder (dx_prmry_clinical_classification = "Bipolar and related disorders")

*	Major Depression (dx_prmry_clinical_classification = "Depressive disorders")

*	Post-Traumatic Stress Disorder (dx_prmry_clinical_classification = "Trauma- and stressor-related disorders")

*	Borderline Personality Disorder (dx_prmry_clinical_classification = "Personality disorders")

*	Obsessive-Compulsive Disorder (dx_prmry_clinical_classification = "Obsessive-compulsive and related disorders", "Disruptive, impulse-control and conduct disorder")

*	Panic Disorder (nothing coded)

*	Phobias (nothing coded)

*	Eating Disorders (nothing coded)

*	I also included the following diagnoses because it seems like they fit within the definition: dx_prmry_clinical_classification = "Mood disorders" or "Other specified and unspecified mood disorders"


```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_smi_opioid_hu_grouping <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(hu_group_overall) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ SMI Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_smi_flag==1]),
                   `Individuals w/ SMI Primary Diagnosis (%)` = scales::percent(`Individuals w/ SMI Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ Opioid-related Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_opioid_related_flag==1]),
                   `Individuals w/ Opioid-related Primary Diagnosis (%)` = scales::percent(`Individuals w/ Opioid-related Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`)) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Status` = hu_group_overall) 

# statewide
medicaid_jail_smi_opioid_statewide <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ SMI Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_smi_flag==1]),
                   `Individuals w/ SMI Primary Diagnosis (%)` = scales::percent(`Individuals w/ SMI Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ Opioid-related Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_opioid_related_flag==1]),
                   `Individuals w/ Opioid-related Primary Diagnosis (%)` = scales::percent(`Individuals w/ Opioid-related Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`)) %>% 
  dplyr::mutate(`High Utilizer Status` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_smi_opioid_hu_grouping_statewide_table <- rbind(medicaid_jail_smi_opioid_hu_grouping,
                                                               medicaid_jail_smi_opioid_statewide)

### print table via kableextra
kable(medicaid_jail_smi_opioid_hu_grouping_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  scroll_box(width = "130%")

```

<br><br>

### Table 4b: Percentage of Individuals with SMI or Opioid-related Primary Diagnoses (Individual-level)

This table explores the percentage of individuals in the sample with SMI or Opioid-related primary diagnoses, based on the following slides in the powerpoint: 

* Slide 38: A closer look at serious SMI's (bipolar disorder, schizophrenia, etc.) 

* Slide 40: HU's ____% more likely to have an opioid use disorder

**See full notes and business rules for variable creation in data dictionary for individual-level analytic file here: https://csgorg.sharepoint.com/:x:/s/Team-JC-Research/EUJfEABIuNNBvKARa4Kq1nwBvSLwsK4aH7K9oZDOWxbc1w?e=zLytTB**


**Update**: Percentages reflect the percentage of the Medicaid sample unless otherwise stated (e.g. "% of Overall Sample"). I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during the study period. The following primary diagnoses are coded as "SMI" -- based on National Alliance on Mental Illness New Hampshire's definition (NAMI NH), which David shared:

*	Schizophrenia (dx_prmry_clinical_classification = "Schizophrenia and other psychotic disorders", "Schizophrenia spectrum and other psychotic disorders")

*	Bipolar Disorder (dx_prmry_clinical_classification = "Bipolar and related disorders")

*	Major Depression (dx_prmry_clinical_classification = "Depressive disorders")

*	Post-Traumatic Stress Disorder (dx_prmry_clinical_classification = "Trauma- and stressor-related disorders")

*	Borderline Personality Disorder (dx_prmry_clinical_classification = "Personality disorders")

*	Obsessive-Compulsive Disorder (dx_prmry_clinical_classification = "Obsessive-compulsive and related disorders", "Disruptive, impulse-control and conduct disorder")

*	Panic Disorder (nothing coded)

*	Phobias (nothing coded)

*	Eating Disorders (nothing coded)

*	I also included the following diagnoses because it seems like they fit within the definition: dx_prmry_clinical_classification = "Mood disorders" or "Other specified and unspecified mood disorders"


```{r echo=FALSE,message=FALSE,warning=FALSE} 
# by hu_group_exclusive
medicaid_jail_smi_opioid_hu_grouping <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(hu_group_exclusive) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ SMI Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_smi_flag==1]),
                   `Individuals w/ SMI Primary Diagnosis (%)` = scales::percent(`Individuals w/ SMI Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ Opioid-related Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_opioid_related_flag==1]),
                   `Individuals w/ Opioid-related Primary Diagnosis (%)` = scales::percent(`Individuals w/ Opioid-related Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`)) %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 

# statewide
medicaid_jail_smi_opioid_statewide <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[pre_or_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ any Medicaid Match (% of Overall Sample)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[pre_or_study_mh_service_primary_dx_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ SMI Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_smi_flag==1]),
                   `Individuals w/ SMI Primary Diagnosis (%)` = scales::percent(`Individuals w/ SMI Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`),
                   `Individuals w/ Opioid-related Primary Diagnosis (N)` = n_distinct(unique_person_id[pre_or_study_opioid_related_flag==1]),
                   `Individuals w/ Opioid-related Primary Diagnosis (%)` = scales::percent(`Individuals w/ Opioid-related Primary Diagnosis (N)`/`Individuals w/ any Medicaid Match (N)`)) %>% 
  dplyr::mutate(`High Utilizer Percentiles` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_smi_opioid_hu_grouping_statewide_table <- rbind(medicaid_jail_smi_opioid_hu_grouping,
                                                               medicaid_jail_smi_opioid_statewide)

### print table via kableextra
kable(medicaid_jail_smi_opioid_hu_grouping_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  scroll_box(width = "130%")

```

<br><br>


## Visuals


### Visual 1: Distribution of ED Visits across New Hampshire

Note: This plot explores the handful of outliers that appear in the Medicaid data (e.g., 100+ ED visits). For ease of interpretation, I've removed all individuals with 0 ED Visits (the vast majority at 6,000+) as well as extreme outliers (150+ visits; there are about 20 individuals with more than 105 visits recorded, though some counts seem erroneously high) 

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during the study period


```{r layout="l-body-outset", echo=FALSE,message=FALSE,warning=FALSE} 
### create a new variable with the specified quantiles
plot_ed_visits_statewide_distribution <- jail_medicaid_analytic_individual_booking_level_dedup_ed_visit_count_recode %>%
  filter(pre_or_study_window_medicaid_match_flag_overall==1,
         pre_or_study_ed_visit_or_service_encounter_count!=0,
         pre_or_study_ed_visit_or_service_encounter_count<105) %>% 
  mutate(county_name_short = paste0(stringr::str_extract(county, "^.{4}"),"."))
  

ggplot(data = plot_ed_visits_statewide_distribution,
       aes(x=pre_or_study_ed_visit_or_service_encounter_count)) +
    geom_histogram(binwidth=1, fill="#007392", color="#e9ecef", alpha=0.9) +
    theme_minimal(20, base_family = "Calibri") +
  theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = "Number of Individuals", x = "Number of ED Visits",
      caption = NULL,
      title = NULL,
      subtitle = NULL) 

```

<br><br>

### Visual 2: Distribution of ED Visits by High Utilizer Grouping

Note: This plot explores the handful of outliers that appear in the Medicaid data (e.g., 100+ ED visits). For ease of interpretation, I've removed all individuals with 0 ED Visits (the vast majority at 6,000+) as well as extreme outliers (150+ visits; there are about 20 individuals with more than 105 visits recorded, though some counts seem erroneously high) 

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during the study period

```{r layout="l-body-outset", echo=FALSE,message=FALSE,warning=FALSE} 
ggplot(data = plot_ed_visits_statewide_distribution,
       aes(x=pre_or_study_ed_visit_or_service_encounter_count)) +
    geom_histogram(binwidth=1, fill="#007392", color="#e9ecef", alpha=0.9) +
  facet_grid(hu_group_exclusive ~ ., scales = "free") +
    theme_minimal(20, base_family = "Calibri") +
  theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = "Number of Individuals", x = "Number of ED Visits",
      caption = NULL,
      title = NULL,
      subtitle = NULL) 

```

<br><br>

### Visual 3: Distribution of ED Visits by County

Note: This plot explores the handful of outliers that appear in the Medicaid data (e.g., 100+ ED visits). For ease of interpretation, I've removed all individuals with 0 ED Visits (the vast majority at 6,000+) as well as extreme outliers (150+ visits; there are about 20 individuals with more than 105 visits recorded, though some counts seem erroneously high) 

**Update**: I am currently using all behavioral health data from the Medicaid Encounter file that occurred either before or during the study period

```{r layout="l-body-outset", echo=FALSE,message=FALSE,warning=FALSE} 
ggplot(data = plot_ed_visits_statewide_distribution,
       aes(x=pre_or_study_ed_visit_or_service_encounter_count)) +
    geom_histogram(binwidth=1, fill="#007392", color="#e9ecef", alpha=0.9) +
  facet_grid(county_name_short ~ ., scales = "free") +
    theme_minimal(20, base_family = "Calibri") +
  theme(panel.grid.major = element_blank(),
          # panel.grid.minor = element_blank(),
          axis.line=element_blank(),
          legend.position = "top",
        legend.title.align=0.5,
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    labs(y = "Number of Individuals", x = "Number of ED Visits",
      caption = NULL,
      title = NULL,
      subtitle = NULL) 

```

<br><br>

