---
title: "Medicaid Trends"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","csgjcr","distill","tidylog")

```

```{r include=FALSE}
### set chunk output 
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  dev = "ragg_png",
  cache = FALSE
  )

### set path using csg_sp_path
sp_data_path <- csg_sp_path(file.path("JR_NH"))

```

```{r include=FALSE}
### import adm_all -- jail administrative that we'll compare to the numbers from the medicaid match files
load(paste0(sp_data_path, "/Data/r_data/adm_all.Rda", 
            sep = "")) 

### de-dup by individual and booking -- these are the two units of analysis for comparisons to the medicaid data
### here we are de-duping bookings with multiple charges as we don't need that information for this comparison
adm_all_dedup <- adm_all %>% 
  ungroup() %>% 
  distinct(id, 
           booking_id,
           .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(id,
                                    booking_id)) ### creating unique booking id with both individual and booking IDs


### import medicaid_jail_all -- medicaid jail data that we'll compare to the numbers from the jail administrative files
### this file lives on the external hard drive (created and exported in `14_medicaid.R`)
medicaid_jail_all <- read_rds("D:/Analytic/medicaid_jail_all.rds") 

### de-dup (there are a few duplicate bookings) and create booking id for analysis
medicaid_jail_all_dedup <- medicaid_jail_all %>% 
  distinct(unique_person_id, 
           booking_id,
           .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(unique_person_id,
                                    booking_id)) ### creating unique booking id with both individual and booking IDs

### import jail_medicaid_analytic_individual_booking_level -- the individual-level analytic file created with all DHHS files
### file is unique by individual/booking
### this file lives on the external hard drive (created and exported in `14_medicaid.R`)
jail_medicaid_analytic_individual_booking_level <- read_rds("D:/Analytic/jail_medicaid_analytic_individual_booking_level.rds") 

### de-dup (there are a few duplicate bookings) and create booking id for analysis
jail_medicaid_analytic_individual_booking_level_dedup <- jail_medicaid_analytic_individual_booking_level %>% 
  distinct(unique_person_id, 
           booking_id,
           .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(unique_person_id,
                                    booking_id)) ### creating unique booking id with both individual and booking IDs
```         

# Medicaid Data Descriptives


## Table 1. Data Check: Unique Individuals and Bookings in Administrative Jail Data versus Medicaid Jail Data

Note: With Medicaid data, the count of unique individuals in each jail will not add up to the statewide total as some individuals were booked at multiple jails. Thus, they appear in multiple individual jail counts, but only once in the statewide count. For this reason, it is probably best to only compare differences in unique individuals at the jail-level. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create table of unique individuals and bookings by county using the adm_all_dedup file

# by county
adm_all_dedup_county_table <- adm_all_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Unique Individuals, Jail Data (N)` = n_distinct(id),
                   `Unique Bookings, Jail Data (N)` = n_distinct(unique_person_booking_id))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
adm_all_dedup_overall_table <- adm_all_dedup %>% 
  dplyr::summarise(`Unique Individuals, Jail Data (N)` = n_distinct(id),
                   `Unique Bookings, Jail Data (N)` = n_distinct(unique_person_booking_id))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# join county and statewide files 
adm_all_dedup_county_statewide_count_table <- rbind(adm_all_dedup_county_table,
                                                    adm_all_dedup_overall_table)

### create table of unique individuals and bookings by county using the medicaid_jail_all file

# by county
medicaid_jail_all_county_table <- medicaid_jail_all_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Unique Individuals, Medicaid Data (N)` = n_distinct(unique_person_id),
                   `Unique Bookings, Medicaid Data (N)` = n_distinct(unique_person_booking_id))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
medicaid_jail_all_overall_table <- medicaid_jail_all_dedup %>% 
  dplyr::summarise(`Unique Individuals, Medicaid Data (N)` = n_distinct(unique_person_id),
                   `Unique Bookings, Medicaid Data (N)` = n_distinct(unique_person_booking_id))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# join county and statewide files 
medicaid_jail_all_county_statewide_count_table <- rbind(medicaid_jail_all_county_table,
                                                    medicaid_jail_all_overall_table)

### now cbind adm_all_dedup_county_statewide_count_table and medicaid_jail_all_county_statewide_count_table
jail_adm_medicaid_count_table <- inner_join(adm_all_dedup_county_statewide_count_table,
                                       medicaid_jail_all_county_statewide_count_table,
                                       by = "Jail") %>% 
  mutate(`Difference in Unique Individuals (N)` = abs(`Unique Individuals, Jail Data (N)` - `Unique Individuals, Medicaid Data (N)`),
         `Difference in Unique Bookings (N)` = abs(`Unique Bookings, Jail Data (N)` - `Unique Bookings, Medicaid Data (N)`)) %>% 
  dplyr::select(`Jail`,
                `Unique Individuals, Jail Data (N)`,
                `Unique Individuals, Medicaid Data (N)`,
                `Difference in Unique Individuals (N)`,
                `Unique Bookings, Jail Data (N)`,
                `Unique Bookings, Medicaid Data (N)`,
                `Difference in Unique Bookings (N)`) 
  
### print table via kableextra
kable(jail_adm_medicaid_count_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(7, bold = TRUE)
```

<br><br>

## Table 2. Percentage of Individuals/Bookings with Medicaid Match and Behavioral Health "Encounters"

Note: "Encounters" include any behavioral health-related medical/clinical or pharmacy visitation. Examples include ED visits or pharmacy services linked to mental health or substance use disorder diagnoses. We should probably ask Uma for a DHHS definition for the presentation. I am currently using all behavioral health data from the Medicaid Encounter file, regardless of timing (before, during, or after the study period)

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create table of highlighting the percentage of the medicaid sample that is matched to medicaid data (using medicaid_match_flag) by county using the medicaid_jail_all file

# by county
medicaid_jail_percent_match_county_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`),
                   `Overall Bookings (N)` = n_distinct(unique_person_id,
                                                      booking_id),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ Medicaid Match (%)` = scales::percent(`Bookings w/ Medicaid Match (N)`/`Overall Bookings (N)`),
                   `Bookings w/ BH Encounter (N)` = n_distinct(unique_person_booking_id[overall_bh_flag==1]),
                   `Bookings w/ BH Encounter (%)` = scales::percent(`Bookings w/ BH Encounter (N)`/`Overall Bookings (N)`))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
medicaid_jail_percent_match_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
   dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`),
                   `Overall Bookings (N)` = n_distinct(unique_person_id,
                                                      booking_id),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ Medicaid Match (%)` = scales::percent(`Bookings w/ Medicaid Match (N)`/`Overall Bookings (N)`),
                   `Bookings w/ BH Encounter (N)` = n_distinct(unique_person_booking_id[overall_bh_flag==1]),
                   `Bookings w/ BH Encounter (%)` = scales::percent(`Bookings w/ BH Encounter (N)`/`Overall Bookings (N)`))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_percent_match_county_statewide_table <- rbind(medicaid_jail_percent_match_county_table,
                                                    medicaid_jail_percent_match_overall_table)

### print table via kableextra
kable(medicaid_jail_percent_match_county_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(9, bold = TRUE) %>% 
  column_spec(11, bold = TRUE)
```

<br><br>

## Table 3. Percentage of Individuals/Bookings with Medicaid Match and Behavioral Health "Encounters": by timing of BH Encounter

Note: "Encounters" include any behavioral health-related medical/clinical or pharmacy visitation. Examples include ED visits or pharmacy services linked to mental health or substance use disorder diagnoses. We should probably ask Uma for a DHHS definition for the presentation. 

**The following table is split out by timing of behavioral health Medicaid encounter: before, during, or after the study period. See logic below**

Pre-study period: Medicaid eligibility end date < 7/1/2018

Study period: Medicaid eligibility end date >= 7/1/2018 & Medicaid eligibility start date <= 6/30/2021

Post-study period: Medicaid eligibility start date > 6/30/2021 (b/c this was a very small sample, I have only presented pre- and study-window counts and percentages)

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create table of highlighting the percentage of the medicaid sample that is matched to medicaid data (using medicaid_match_flag) by county using the medicaid_jail_all file -- by timing of medicaid enrollment and BH encounters relative to jail admin sample/study window

# by county
medicaid_jail_percent_match_county_timing_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ any Medicaid Match (%)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ Medicaid Match, Pre-Study (N)` = n_distinct(unique_person_id[pre_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ Medicaid Match, Pre-Study (%)` = scales::percent(`Individuals w/ Medicaid Match, Pre-Study (N)`/`Overall Individuals (N)`),
                   `Individuals w/ Medicaid Match, Study Window (N)` = n_distinct(unique_person_id[study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ Medicaid Match, Study Window (%)` = scales::percent(`Individuals w/ Medicaid Match, Study Window (N)`/`Overall Individuals (N)`),
                   `Individuals w/ any BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ any BH Encounter (%)` = scales::percent(`Individuals w/ any BH Encounter (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter, Pre-Study (N)` = n_distinct(unique_person_id[pre_bh_flag==1]),
                   `Individuals w/ BH Encounter, Pre-Study (%)` = scales::percent(`Individuals w/ BH Encounter, Pre-Study (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter, Study Window (N)` = n_distinct(unique_person_id[study_bh_flag==1]),
                   `Individuals w/ BH Encounter, Study Window (%)` = scales::percent(`Individuals w/ BH Encounter, Study Window (N)`/`Overall Individuals (N)`))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
medicaid_jail_percent_match_overall_timing_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ any Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ any Medicaid Match (%)` = scales::percent(`Individuals w/ any Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ Medicaid Match, Pre-Study (N)` = n_distinct(unique_person_id[pre_study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ Medicaid Match, Pre-Study (%)` = scales::percent(`Individuals w/ Medicaid Match, Pre-Study (N)`/`Overall Individuals (N)`),
                   `Individuals w/ Medicaid Match, Study Window (N)` = n_distinct(unique_person_id[study_window_medicaid_match_flag_overall==1]),
                   `Individuals w/ Medicaid Match, Study Window (%)` = scales::percent(`Individuals w/ Medicaid Match, Study Window (N)`/`Overall Individuals (N)`),
                   `Individuals w/ any BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ any BH Encounter (%)` = scales::percent(`Individuals w/ any BH Encounter (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter, Pre-Study (N)` = n_distinct(unique_person_id[pre_bh_flag==1]),
                   `Individuals w/ BH Encounter, Pre-Study (%)` = scales::percent(`Individuals w/ BH Encounter, Pre-Study (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter, Study Window (N)` = n_distinct(unique_person_id[study_bh_flag==1]),
                   `Individuals w/ BH Encounter, Study Window (%)` = scales::percent(`Individuals w/ BH Encounter, Study Window (N)`/`Overall Individuals (N)`))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_percent_match_county_statewide_timing_table <- rbind(medicaid_jail_percent_match_county_timing_table,
                                                    medicaid_jail_percent_match_overall_timing_table)

### print table via kableextra
kable(medicaid_jail_percent_match_county_statewide_timing_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(8, bold = TRUE) %>% 
  column_spec(10, bold = TRUE) %>% 
  column_spec(12, bold = TRUE) %>% 
  column_spec(14, bold = TRUE)
```

<br><br>

## Table 4. Percentage of High Utilizer Individuals with Medicaid Match and Behavioral Health "Encounters"

Note: "Encounters" include any behavioral health-related medical/clinical or pharmacy visitation. Examples include ED visits or pharmacy services linked to mental health or substance use disorder diagnoses. We should probably ask Uma for a DHHS definition for the presentation. I am currently using all behavioral health data from the Medicaid Encounter file, regardless of timing (before, during, or after the study period)

Grouping of individuals into 'high utilizer' percentile groups is based on statewide data, using the Medicaid match files from DHHS, as opposed to county-level data. In other words 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### to recode high utlizer percentile grouping, we don't need to group_by as the percentile grouping is already grouped across individual from Mari's cleaning
jail_medicaid_analytic_individual_booking_level_dedup_hu_recode <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  ### to ensure each individual/booking is in correct grouping, start with Non-HU, then 10% and move down to 1%
  mutate(hu_group_exclusive = case_when(
    high_utilizer_10_pct=="No" ~ 4,
    high_utilizer_10_pct=="Yes" & high_utilizer_5_pct=="No" & high_utilizer_1_pct=="No" ~ 3,
    high_utilizer_5_pct=="Yes" & high_utilizer_1_pct=="No" ~ 2,
    high_utilizer_1_pct=="Yes" ~ 1,
    TRUE ~ as.numeric(NA)),
    hu_group_exclusive = factor(hu_group_exclusive,
         levels = c(1,2,3,4),
         labels = c("Top 1%", "Top 5%", "Top 10%", "Non-HU")))

### create table of highlighting the percentage of the medicaid sample that is matched to medicaid data (using medicaid_match_flag) by county using the medicaid_jail_all file

# by county
medicaid_jail_percent_match_high_util_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(hu_group_exclusive) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`))  %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 

# statewide
medicaid_jail_percent_match_high_util_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
   dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`))  %>% 
  dplyr::mutate(`High Utilizer Percentiles` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_percent_match_high_util_statewide_table <- rbind(medicaid_jail_percent_match_high_util_table,
                                                    medicaid_jail_percent_match_high_util_overall_table)

### print table via kableextra
kable(medicaid_jail_percent_match_high_util_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) 

```

<br><br>

## Table 5. Percentage of Individuals/Bookings who were Experiencing Homelessness at time of Medicaid Eligibility

Note: Since we only have homelessness data for individuals who matched to Medicaid enrollment data, our denominator for these metrics will be the sample of individuals who have at least one Medicaid enrollment during the study window (i.e., individuals who did not match to Medicaid data are excluded here). Because of this decision as well as the fact that the DHHS data notes whether an individual was experiencing homelessness at the beginning of a given Medicaid enrollment period. In other words, we wouldn't know if someone had housing at the beginning of enrollment and then experienced homelessness afterwards). I am currently using all homelessness data from the Medicaid Enrollment files, regardless of timing (before, during, or after the study period). 

**Because of these factors, we should all discuss how we understand and explain this measure. At the very least, we probably want to acknowledge that this is likely an under count** 


```{r echo=FALSE,message=FALSE,warning=FALSE}
### create table of highlighting the percentage of the medicaid sample that experienced homelessness at the beginning of any medicaid enrollment period in DHHS pull

# by county
medicaid_jail_homelessness_county_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ any experience of homelessness (N)` = n_distinct(unique_person_id[pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1]),
                   `Individuals w/ any experience of homelessness (%)` = scales::percent(`Individuals w/ any experience of homelessness (N)`/`Individuals w/ Medicaid Match (N)`),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ any experience of homelessness (N)` = n_distinct(unique_person_booking_id[pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1]),
                   `Bookings w/ any experience of homelessness (%)` = scales::percent(`Bookings w/ any experience of homelessness (N)`/`Bookings w/ Medicaid Match (N)`))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
medicaid_jail_homelessness_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
   dplyr::summarise(`Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ any experience of homelessness (N)` = n_distinct(unique_person_id[pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1]),
                   `Individuals w/ any experience of homelessness (%)` = scales::percent(`Individuals w/ any experience of homelessness (N)`/`Individuals w/ Medicaid Match (N)`),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ any experience of homelessness (N)` = n_distinct(unique_person_booking_id[pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1]),
                   `Bookings w/ any experience of homelessness (%)` = scales::percent(`Bookings w/ any experience of homelessness (N)`/`Bookings w/ Medicaid Match (N)`))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_homelessness_county_statewide_table <- rbind(medicaid_jail_homelessness_county_table,
                                                    medicaid_jail_homelessness_overall_table)

### print table via kableextra
kable(medicaid_jail_homelessness_county_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(7, bold = TRUE)

```

<br><br>

## Table 6. Percentage of High Utilizer Individuals/Bookings who were Experiencing Homelessness at time of Medicaid Eligibility

Note: Since we only have homelessness data for individuals who matched to Medicaid enrollment data, our denominator for these metrics will be the sample of individuals who have at least one Medicaid enrollment during the study window (i.e., individuals who did not match to Medicaid data are excluded here). Because of this decision as well as the fact that the DHHS data notes whether an individual was experiencing homelessness at the beginning of a given Medicaid enrollment period. In other words, we wouldn't know if someone had housing at the beginning of enrollment and then experienced homelessness afterwards). I am currently using all homelessness data from the Medicaid Enrollment files, regardless of timing (before, during, or after the study period). 

**Because of these factors, we should all discuss how we understand and explain this measure. At the very least, we probably want to acknowledge that this is likely an under count** 

**Statistics for individuals who are high utilizers of jail are based on the top 10% percentile of statewide bookings.**


```{r echo=FALSE,message=FALSE,warning=FALSE}
### create table of highlighting the percentage of the medicaid sample that experienced homelessness at the beginning of any medicaid enrollment period in DHHS pull

# by county
medicaid_jail_homelessness_hu_county_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::group_by(hu_group_exclusive) %>% 
  dplyr::summarise(`Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ any experience of homelessness (N)` = n_distinct(unique_person_id[(pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1)]),
                   `Individuals w/ any experience of homelessness (%)` = scales::percent(`Individuals w/ any experience of homelessness (N)`/`Individuals w/ Medicaid Match (N)`),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ any experience of homelessness (N)` = n_distinct(unique_person_booking_id[(pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1)]),
                   `Bookings w/ any experience of homelessness (%)` = scales::percent(`Bookings w/ any experience of homelessness (N)`/`Bookings w/ Medicaid Match (N)`))  %>% 
  ungroup() %>% 
  dplyr::rename(`High Utilizer Percentiles` = hu_group_exclusive) 

# statewide
medicaid_jail_homelessness_hu_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup_hu_recode %>% 
  dplyr::summarise(`Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ any experience of homelessness (N)` = n_distinct(unique_person_id[(pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1)]),
                   `Individuals w/ any experience of homelessness (%)` = scales::percent(`Individuals w/ any experience of homelessness (N)`/`Individuals w/ Medicaid Match (N)`),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ any experience of homelessness (N)` = n_distinct(unique_person_booking_id[(pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1)]),
                   `Bookings w/ any experience of homelessness (%)` = scales::percent(`Bookings w/ any experience of homelessness (N)`/`Bookings w/ Medicaid Match (N)`))  %>%  
  dplyr::mutate(`High Utilizer Percentiles` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_homelessness_hu_county_statewide_table <- rbind(medicaid_jail_homelessness_hu_county_table,
                                                    medicaid_jail_homelessness_hu_overall_table)

### print table via kableextra
kable(medicaid_jail_homelessness_hu_county_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(7, bold = TRUE)

```

<br><br>

## Table 7. Percentage of Behavioral Health "Encounters" by Treatment, Service, and Programming Type

Note: "Encounters" include any behavioral health-related medical/clinical or pharmacy visitation. Examples include ED visits or pharmacy services linked to mental health or substance use disorder diagnoses. We should probably ask Uma for a DHHS definition for the presentation. I am currently using all behavioral health data from the Medicaid Encounter file, regardless of timing (before, during, or after the study period). For this analysis, encounter type is broken down into mental health, substance use disorder, whether service is affiliated with CMHC provider (Community Mental Health Centers), emergency department visit, pharmacy service for mental health, pharmacy service for substance use disorder, as well as other services. 

```{r echo=FALSE,message=FALSE,warning=FALSE} 
### create table of highlighting the percentage of the medicaid sample that is matched to medicaid data (using medicaid_match_flag) by county using the medicaid_jail_all file

# by county
medicaid_jail_percent_match_county_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`),
                   `Overall Bookings (N)` = n_distinct(unique_person_id,
                                                      booking_id),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ Medicaid Match (%)` = scales::percent(`Bookings w/ Medicaid Match (N)`/`Overall Bookings (N)`),
                   `Bookings w/ BH Encounter (N)` = n_distinct(unique_person_booking_id[overall_bh_flag==1]),
                   `Bookings w/ BH Encounter (%)` = scales::percent(`Bookings w/ BH Encounter (N)`/`Overall Bookings (N)`))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
medicaid_jail_percent_match_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
   dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`),
                   `Overall Bookings (N)` = n_distinct(unique_person_id,
                                                      booking_id),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ Medicaid Match (%)` = scales::percent(`Bookings w/ Medicaid Match (N)`/`Overall Bookings (N)`),
                   `Bookings w/ BH Encounter (N)` = n_distinct(unique_person_booking_id[overall_bh_flag==1]),
                   `Bookings w/ BH Encounter (%)` = scales::percent(`Bookings w/ BH Encounter (N)`/`Overall Bookings (N)`))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_percent_match_county_statewide_table <- rbind(medicaid_jail_percent_match_county_table,
                                                    medicaid_jail_percent_match_overall_table)

### print table via kableextra
kable(medicaid_jail_percent_match_county_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(9, bold = TRUE) %>% 
  column_spec(11, bold = TRUE)
```

<br><br>

**Next steps:**

What treatment, programming, or services did high utilizers receive in the community (via Medicaid) from 2019 to 2021?
- Parse out all study flags here -- for entire medicaid match population and then by HU grouping (do we have a NH-general population estimate for comparison?) + ED counts



**Additional Analyses for second encounter-level analytic file:**

* Slide 38: A closer look at serious SPMI's (bipolar disorder, schizophrenia, etc.) 

* Slide 40: HU's ____% more likely to have an opioid use disorder

* Slide 43: From 2019 to 2021, service providers were reimbursed X% less than the national average.From 2019 to 2021, service providers were reimbursed an average of $X per claim.

* Is Medicaid enrollment starting again when people are released from jail? 


<br><br>

