---
title: "Medicaid Trends"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","csgjcr","distill","tidylog")

```

```{r include=FALSE}
### set chunk output 
knitr::opts_chunk$set(
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE,
  dev = "ragg_png",
  cache = FALSE
  )

### set path using csg_sp_path
sp_data_path <- csg_sp_path(file.path("JR_NH"))

```

```{r include=FALSE}
### import adm_all -- jail administrative that we'll compare to the numbers from the medicaid match files
load(paste0(sp_data_path, "/Data/r_data/adm_all.Rda", 
            sep = "")) 

### de-dup by individual and booking -- these are the two units of analysis for comparisons to the medicaid data
### here we are de-duping bookings with multiple charges as we don't need that information for this comparison
adm_all_dedup <- adm_all %>% 
  ungroup() %>% 
  distinct(id, 
           booking_id,
           .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(id,
                                    booking_id)) ### creating unique booking id with both individual and booking IDs


### import medicaid_jail_all -- medicaid jail data that we'll compare to the numbers from the jail administrative files
### this file lives on the external hard drive (created and exported in `14_medicaid.R`)
medicaid_jail_all <- read_rds("D:/Analytic/medicaid_jail_all.rds") 

### de-dup (there are a few duplicate bookings) and create booking id for analysis
medicaid_jail_all_dedup <- medicaid_jail_all %>% 
  distinct(unique_person_id, 
           booking_id,
           .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(unique_person_id,
                                    booking_id)) ### creating unique booking id with both individual and booking IDs

### import jail_medicaid_analytic_individual_booking_level -- the individual-level analytic file created with all DHHS files
### file is unique by individual/booking
### this file lives on the external hard drive (created and exported in `14_medicaid.R`)
jail_medicaid_analytic_individual_booking_level <- read_rds("D:/Analytic/jail_medicaid_analytic_individual_booking_level.rds") 

### de-dup (there are a few duplicate bookings) and create booking id for analysis
jail_medicaid_analytic_individual_booking_level_dedup <- jail_medicaid_analytic_individual_booking_level %>% 
  distinct(unique_person_id, 
           booking_id,
           .keep_all = TRUE) %>% 
  mutate(unique_person_booking_id = paste0(unique_person_id,
                                    booking_id)) ### creating unique booking id with both individual and booking IDs
```         

# Medicaid Data Descriptives


## Table 1. Data Check: Unique individuals and bookings in administrative jail data versus Medicaid jail data

Note: With Medicaid data, the count of unique individuals in each jail will not add up to the statewide total as some individuals were booked at multiple jails. Thus, they appear in multiple individual jail counts, but only once in the statewide count. For this reason, it is probably best to only compare differences in unique individuals at the jail-level. 

**To figure out: carroll + cheshire differences?**

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create table of unique individuals and bookings by county using the adm_all_dedup file

# by county
adm_all_dedup_county_table <- adm_all_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Unique Individuals, Jail Data (N)` = n_distinct(id),
                   `Unique Bookings, Jail Data (N)` = n_distinct(unique_person_booking_id))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
adm_all_dedup_overall_table <- adm_all_dedup %>% 
  dplyr::summarise(`Unique Individuals, Jail Data (N)` = n_distinct(id),
                   `Unique Bookings, Jail Data (N)` = n_distinct(unique_person_booking_id))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# join county and statewide files 
adm_all_dedup_county_statewide_count_table <- rbind(adm_all_dedup_county_table,
                                                    adm_all_dedup_overall_table)

### create table of unique individuals and bookings by county using the medicaid_jail_all file

# by county
medicaid_jail_all_county_table <- medicaid_jail_all_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Unique Individuals, Medicaid Data (N)` = n_distinct(unique_person_id),
                   `Unique Bookings, Medicaid Data (N)` = n_distinct(unique_person_booking_id))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
medicaid_jail_all_overall_table <- medicaid_jail_all_dedup %>% 
  dplyr::summarise(`Unique Individuals, Medicaid Data (N)` = n_distinct(unique_person_id),
                   `Unique Bookings, Medicaid Data (N)` = n_distinct(unique_person_booking_id))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# join county and statewide files 
medicaid_jail_all_county_statewide_count_table <- rbind(medicaid_jail_all_county_table,
                                                    medicaid_jail_all_overall_table)

### now cbind adm_all_dedup_county_statewide_count_table and medicaid_jail_all_county_statewide_count_table
jail_adm_medicaid_count_table <- inner_join(adm_all_dedup_county_statewide_count_table,
                                       medicaid_jail_all_county_statewide_count_table,
                                       by = "Jail") %>% 
  mutate(`Difference in Unique Individuals (N)` = abs(`Unique Individuals, Jail Data (N)` - `Unique Individuals, Medicaid Data (N)`),
         `Difference in Unique Bookings (N)` = abs(`Unique Bookings, Jail Data (N)` - `Unique Bookings, Medicaid Data (N)`)) %>% 
  dplyr::select(`Jail`,
                `Unique Individuals, Jail Data (N)`,
                `Unique Individuals, Medicaid Data (N)`,
                `Difference in Unique Individuals (N)`,
                `Unique Bookings, Jail Data (N)`,
                `Unique Bookings, Medicaid Data (N)`,
                `Difference in Unique Bookings (N)`) 
  
### print table via kableextra
kable(jail_adm_medicaid_count_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(7, bold = TRUE)
```

<br><br>

## Table 2. Percentage of individuals/bookings with Medicaid Match and Behavior Health "Encounters"

Note: "Encounters" include any behavioral health-related medical/clinical or pharmacy visitation. Examples include ED visits or pharmacy services linked to mental health or substance use disorder diagnoses. We should probably ask Uma for a DHHS definition for the presentation. I am currently using all behavioral health data from the Medicaid Encounter file, regardless of timing (before, during, or after the study period)

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create table of highlighting the percentage of the medicaid sample that is matched to medicaid data (using medicaid_match_flag) by county using the medicaid_jail_all file

# by county
medicaid_jail_percent_match_county_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`),
                   `Overall Bookings (N)` = n_distinct(unique_person_id,
                                                      booking_id),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ Medicaid Match (%)` = scales::percent(`Bookings w/ Medicaid Match (N)`/`Overall Bookings (N)`),
                   `Bookings w/ BH Encounter (N)` = n_distinct(unique_person_booking_id[overall_bh_flag==1]),
                   `Bookings w/ BH Encounter (%)` = scales::percent(`Bookings w/ BH Encounter (N)`/`Overall Bookings (N)`))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
medicaid_jail_percent_match_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
   dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`),
                   `Overall Bookings (N)` = n_distinct(unique_person_id,
                                                      booking_id),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ Medicaid Match (%)` = scales::percent(`Bookings w/ Medicaid Match (N)`/`Overall Bookings (N)`),
                   `Bookings w/ BH Encounter (N)` = n_distinct(unique_person_booking_id[overall_bh_flag==1]),
                   `Bookings w/ BH Encounter (%)` = scales::percent(`Bookings w/ BH Encounter (N)`/`Overall Bookings (N)`))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_percent_match_county_statewide_table <- rbind(medicaid_jail_percent_match_county_table,
                                                    medicaid_jail_percent_match_overall_table)

### print table via kableextra
kable(medicaid_jail_percent_match_county_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(9, bold = TRUE) %>% 
  column_spec(11, bold = TRUE)
```

<br><br>

**TBD**
## Table 3. Percentage of high-utilizer individuals/bookings with Medicaid Match and Behavior Health "Encounters"

Note: "Encounters" include any behavioral health-related medical/clinical or pharmacy visitation. Examples include ED visits or pharmacy services linked to mental health or substance use disorder diagnoses. We should probably ask Uma for a DHHS definition for the presentation. I am currently using all behavioral health data from the Medicaid Encounter file, regardless of timing (before, during, or after the study period)


```{r echo=FALSE,message=FALSE,warning=FALSE}
### create table of highlighting the percentage of the medicaid sample that is matched to medicaid data (using medicaid_match_flag) by county using the medicaid_jail_all file

# by county
medicaid_jail_percent_match_county_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`),
                   `Overall Bookings (N)` = n_distinct(unique_person_id,
                                                      booking_id),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ Medicaid Match (%)` = scales::percent(`Bookings w/ Medicaid Match (N)`/`Overall Bookings (N)`),
                   `Bookings w/ BH Encounter (N)` = n_distinct(unique_person_booking_id[overall_bh_flag==1]),
                   `Bookings w/ BH Encounter (%)` = scales::percent(`Bookings w/ BH Encounter (N)`/`Overall Bookings (N)`))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
medicaid_jail_percent_match_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
   dplyr::summarise(`Overall Individuals (N)` = n_distinct(unique_person_id),
                   `Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ Medicaid Match (%)` = scales::percent(`Individuals w/ Medicaid Match (N)`/`Overall Individuals (N)`),
                   `Individuals w/ BH Encounter (N)` = n_distinct(unique_person_id[overall_bh_flag==1]),
                   `Individuals w/ BH Encounter (%)` = scales::percent(`Individuals w/ BH Encounter (N)`/`Overall Individuals (N)`),
                   `Overall Bookings (N)` = n_distinct(unique_person_id,
                                                      booking_id),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ Medicaid Match (%)` = scales::percent(`Bookings w/ Medicaid Match (N)`/`Overall Bookings (N)`),
                   `Bookings w/ BH Encounter (N)` = n_distinct(unique_person_booking_id[overall_bh_flag==1]),
                   `Bookings w/ BH Encounter (%)` = scales::percent(`Bookings w/ BH Encounter (N)`/`Overall Bookings (N)`))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_percent_match_county_statewide_table <- rbind(medicaid_jail_percent_match_county_table,
                                                    medicaid_jail_percent_match_overall_table)

### print table via kableextra
kable(medicaid_jail_percent_match_county_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(6, bold = TRUE) %>% 
  column_spec(9, bold = TRUE) %>% 
  column_spec(11, bold = TRUE)

```

<br><br>

## Table 4. Percentage of individuals/bookings who were experiencing homelessness at time of Medicaid eligibility

Note: Since we only have homelessness data for individuals who matched to Medicaid enrollment data, our denominator for these metrics will be the sample of individuals who have at least one Medicaid enrollment during the study window (i.e., individuals who did not match to Medicaid data are excluded here). Because of this decision as well as the fact that the DHHS data notes whether an individual was experiencing homelessness at the beginning of a given Medicaid enrollment period. In other words, we wouldn't know if someone had housing at the beginning of enrollment and then experienced homelessness afterwards). I am currently using all homelessness data from the Medicaid Enrollment files, regardless of timing (before, during, or after the study period)

**Because of these factors, we should all discuss how we understand and explain this measure.**


```{r echo=FALSE,message=FALSE,warning=FALSE}
### create table of highlighting the percentage of the medicaid sample that experienced homelessness at the beginning of any medicaid enrollment period in DHHS pull

# by county
medicaid_jail_homelessness_county_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
  dplyr::group_by(county) %>% 
  dplyr::summarise(`Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ any experience of homelessness (N)` = n_distinct(unique_person_id[pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1]),
                   `Individuals w/ any experience of homelessness (%)` = scales::percent(`Individuals w/ any experience of homelessness (N)`/`Individuals w/ Medicaid Match (N)`),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ any experience of homelessness (N)` = n_distinct(unique_person_booking_id[pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1]),
                   `Bookings w/ any experience of homelessness (%)` = scales::percent(`Bookings w/ any experience of homelessness (N)`/`Bookings w/ Medicaid Match (N)`))  %>% 
  ungroup() %>% 
  dplyr::rename(`Jail` = county) 

# statewide
medicaid_jail_homelessness_overall_table <- jail_medicaid_analytic_individual_booking_level_dedup %>% 
   dplyr::summarise(`Individuals w/ Medicaid Match (N)` = n_distinct(unique_person_id[medicaid_match_flag==1]),
                   `Individuals w/ any experience of homelessness (N)` = n_distinct(unique_person_id[pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1]),
                   `Individuals w/ any experience of homelessness (%)` = scales::percent(`Individuals w/ any experience of homelessness (N)`/`Individuals w/ Medicaid Match (N)`),
                   `Bookings w/ Medicaid Match (N)` = n_distinct(unique_person_booking_id[medicaid_match_flag==1]),
                   `Bookings w/ any experience of homelessness (N)` = n_distinct(unique_person_booking_id[pre_homeless_on_eligibility_begin_flag | study_homeless_on_eligibility_begin_flag==1 | post_homeless_on_eligibility_begin_flag==1]),
                   `Bookings w/ any experience of homelessness (%)` = scales::percent(`Bookings w/ any experience of homelessness (N)`/`Bookings w/ Medicaid Match (N)`))  %>% 
  dplyr::mutate(`Jail` = "Statewide") 

# rbind county and statewide files 
medicaid_jail_homelessness_county_statewide_table <- rbind(medicaid_jail_homelessness_county_table,
                                                    medicaid_jail_homelessness_overall_table)

### print table via kableextra
kable(medicaid_jail_homelessness_county_statewide_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE) %>% 
  column_spec(4, bold = TRUE) %>% 
  column_spec(7, bold = TRUE)

```


<br><br>

