---
title: "Mapping NH Resource Need and Availability"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

Here is where we gathered location-level resource information: 

*	Community mental health programs (CMHC): https://www.dhhs.nh.gov/sites/g/files/ehbemt476/files/documents/2021-12/bdas-list-map.pdf
 
I then compiled individual resource locations from each listed organizations’ website


*	Recovery Community Organizations (State-funded RCOs): https://www.dhhs.nh.gov/programs-services/health-care/recovery-support-services

*	DHHS/Bureau of Homeless and Housing Services (BHHS) Cold Weather/Emergency Shelters: https://www.dhhs.nh.gov/programs-services/housing-services/homeless-assistance-prevention-services/shelter-services

* Non-DHHS Funded Shelters/Housing: https://www.dhhs.nh.gov/sites/g/files/ehbemt476/files/documents2/non-dhhs-contracted-emergency-shelters.pdf

* NH Coalition of Recovery Residences: https://www.dhhs.nh.gov/sites/g/files/ehbemt476/files/documents2/nhvregistry.pdf **and** https://www.nhcorr.org/certified-homes

NOTE: NHCORR Certified Recovery Residences are often gender-specific 

```{r include=FALSE,message=FALSE,warning=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","csgjcr","distill","highcharter","censusr")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())
```

```{r include=FALSE,message=FALSE,warning=FALSE}
# Save path
sp_data_path <- csg_get_project_path("NH")

### pull in resource data
nh_resource_locations_raw <- readxl::read_xlsx(file.path(sp_data_path,"Data","nh_resource_map_data.xlsx")) %>% 
  clean_names() %>% 
  mutate(unique_resource_id = paste0(resource_name,row_number())) 


# ### pull idoc supervision level data (# of unique clients who were on supervision level 4 or 5 at some point in 2020 per 10,000 county residents/population)
# 
# ### write out supervision_level_4_5_county_for_map_supervision_race
# supervision_level_4_5_county_for_map_supervision_race <- read_rds(file.path(sharepoint_idoc_resources, "supervision_level_4_5_county_for_map_supervision_race.rds")) %>% 
#   mutate(fips_code = as.character(fips_code))
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### commenting out syntax below because we've already run it and simply need to pull in geocoded data to make knitting more efficient

# ### geocode addresses in nh_resource_locations_raw 
# 
# ### clean address and prepare for geocoding format
# nh_resource_locations_raw_addresses <- nh_resource_locations_raw %>%
#   mutate(street =  gsub("Apt .*","",address)) %>%
#   mutate(street =  gsub("apt .*","",street)) %>%
#   mutate(street =  gsub("Fl .*","",street)) %>%
#   mutate(street =  gsub("Unit .*","",street)) %>%
#   mutate(street =  gsub("\\.","",street)) %>%
#   mutate(zip = as.character(zip),
#          state = "New Hampshire") %>%
#   dplyr::select(unique_resource_id, street, city, state, zip)
# 
# ### obtain lat/lon from address via censusxy::cxy_geocode()
# nh_resource_location_geo <- censusxy::cxy_geocode(nh_resource_locations_raw_addresses, 
#                                                   street = "street", 
#                                                   city = "city", 
#                                                   state = "state", 
#                                                   zip = "zip", 
#                                                   return = "geographies", 
#                                                   benchmark = "Public_AR_Census2020", 
#                                                   vintage = "Census2020_Census2020", 
#                                                   output = "full") %>% 
#   dplyr::select(-c(cxy_address:cxy_tiger_side,cxy_tract_id,cxy_block_id))
# 
# ### seems like we have a pretty good match rate -- but might as well hard code the missing fields
# ### export and then hard code lat/lon for records with missing data using google maps
# 
# ### write out iowa_idoc_resource_facility_geo
# openxlsx::write.xlsx(nh_resource_location_geo,
#           file.path(sp_data_path,"Data",
#                     "nh_resource_location_geo_fix.xlsx"))

## pull file back in now that i've manually geocoded the missing records
nh_resource_location_geo_full <- openxlsx::read.xlsx(file.path(sp_data_path,"Data",
                    "nh_resource_location_geo_fix_with_county.xlsx")) %>%
  dplyr::select(unique_resource_id,lon=cxy_lon,lat=cxy_lat,street,cxy_county_id) %>% 
  right_join(nh_resource_locations_raw, by = "unique_resource_id") %>%
  mutate(resource_type = str_to_title(resource_type)) %>% 
  dplyr::select(-address) %>% 
  ### add county name to geocoded fips county number obtained
  ### see codes here: https://tigerweb.geo.census.gov/tigerwebmain/Files/bas22/tigerweb_bas22_county_nh.html
  mutate(county = case_when(
    cxy_county_id == 1 ~ "Belknap",
    cxy_county_id == 3 ~ "Carroll",
    cxy_county_id == 5 ~ "Cheshire",
    cxy_county_id == 7 ~ "Coos",
    cxy_county_id == 9 ~ "Grafton", 
    cxy_county_id == 11 ~ "Hillsborough", 
    cxy_county_id == 13 ~ "Merrimack", 
    cxy_county_id == 15 ~ "Rockingham", 
    cxy_county_id == 17 ~ "Strafford", 
    cxy_county_id == 19 ~ "Sullivan", 
    TRUE ~ as.character(NA)))
```


```{r include=FALSE,message=FALSE,warning=FALSE}
### pull census/acs data via tidycensus package

### read in census/acs api key from environmnent
### this allows us to pull census/acs data via the tidycensus package
readRenviron("~/.Renviron")

### overall population by county from 2020 census
nh_county_pop_2020 <- tidycensus::get_decennial(geography = "County", 
                                           state = "NH",
                                           variables = "P1_001N",
                                           year = 2020,
                                            geometry = FALSE) %>% 
  clean_names() %>%
  dplyr::select(geoid,name,county_total_pop = value) 

### weighted estimate of percentage of county residents living below federal poverty threshold
nh_poverty_status <- tidycensus::get_acs(geography = "County", 
                                              state = "NH",
                                              variables = "S1701_C03_001", 
                                              geometry = FALSE) %>% 
  clean_names() %>% 
  dplyr::select(geoid,estimate) %>% 
  dplyr::rename(estimate_below_poverty = estimate)

### weighted estimate of income
nh_median_income <- tidycensus::get_acs(geography = "County", 
                                             state = "NH",
                                             variables = "S1901_C01_012", 
                                             geometry = FALSE) %>% 
  clean_names() %>% 
  dplyr::select(geoid,estimate) %>% 
  dplyr::rename(estimate_income = estimate)

### counts of race from 2020 census
### these are the ids of race variables that we want to pull 
race_vars = c(
        all = "P2_001N",
        hispanic = "P2_002N",
        white = "P2_005N",
        black = "P2_006N",
        am_indian = "P2_007N",
        asian = "P2_008N"
        )

iowa_race_2020 <- tidycensus::get_decennial(geography = "County", 
                                               state = "NH",
                                               variables = race_vars, ### use race vars that i've specified
                                               summary_var = "P2_001N", ### summary column for % calculation
                                               year = 2020,
                                               geometry = FALSE) %>% 
  clean_names() %>% 
  mutate(percent = (value/summary_value)*100) ### create percent estimate from estimated counts

### pivot race file to be wide and unique by census tract 
nh_race_2020 %<>%
  dplyr::select(geoid,variable,percent) %>% 
  spread(variable,percent, fill = NA) 
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### join all acs variables together in one file
nh_acs_census_county <- left_join(nh_poverty_status, nh_median_income, by="geoid")

nh_acs_census_county <- left_join(nh_acs_census_county, nh_county_pop_2020, by="geoid")

nh_acs_census_county <- left_join(nh_acs_census_county, nh_race_2020, by="geoid")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### read in county-level iowa data to create county,state, geoid crosswalk with acs/census data 
### this is the official iowa county shapefile, obtained here: https://www.census.gov/geographies/mapping-files/time-series/geo/tiger-line-file.html 
### this is not used for mapping, however, hence we remove geography below; it's just a crosswalk across county name, geoid, and county fip code

### read in nh county-level shape file    
nh_county_shape <- read_sf("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\Geospatial_Mapping\\US County Geo Data\\tl_2019_us_county\\tl_2019_us_county.shp") %>%
  clean_names() %>% 
  filter(statefp=="33") %>% ### filter by state fip code 
  dplyr::rename(county=name, 
                county_fip=countyfp)

### use group_by and st_union to create statewide polygon using the county-level geography
### we'll use this shapefile for a state border when mapping
nh_state_shape <- nh_county_shape %>%
  group_by(statefp) %>% 
  summarize(geometry = st_union(geometry)) %>% 
  ungroup()

### add county name to supervision_level_4_5_county_for_map_supervision_race
supervision_level_4_5_county_for_map_supervision_race_geo <- left_join(supervision_level_4_5_county_for_map_supervision_race,iowa_geo_county,                                                                     by=c("fips_code"="geoid"))
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### merge county code/geoid crosswalk to acs data
iowa_acs_census_county_crosswalk <- inner_join(iowa_acs_census_county,iowa_geo_county,by = "geoid")

### county-level estimates

### clean up acs/census estimates for eventual use as map labels
iowa_acs_census_county_crosswalk_full <- iowa_acs_census_county_crosswalk %>%
    group_by(county_name_short) %>%
    summarize(county_total_pop = sum(county_total_pop, na.rm=TRUE),
              estimate_below_poverty_mean = round(mean(estimate_below_poverty, na.rm=TRUE),digits = 1),
              estimate_income_median = round(mean(estimate_income, na.rm=TRUE),digits = 1),
              percent_asian = round(mean(asian, na.rm=TRUE),digits = 1),
              percent_black = round(mean(black, na.rm=TRUE),digits = 1),
              percent_hispanic = round(mean(hispanic, na.rm=TRUE),digits = 1),
              percent_white = round(mean(white, na.rm=TRUE),digits = 1)) %>%
    ungroup()

### calculate rates using population estimates by county from 2019 American Community Survey
iowa_acs_census_county_no_geo_rates <- iowa_acs_census_county_crosswalk_full %>%
  left_join(supervision_level_4_5_county_for_map_supervision_race_geo, by = "county_name_short") %>%
  group_by(county_name_short) %>%
  mutate(supervision_4_5_2020_rate_per_10000 = round((supervision_4_5_count_2020/county_total_pop)*10000,digits = 4)) %>%
  ungroup() 

```

```{r include=FALSE,message=FALSE,warning=FALSE}
### read in iowa county-level shape file    
iowa_county_shape <- read_sf("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\Geospatial_Mapping\\US County Geo Data\\tl_2019_us_county\\tl_2019_us_county.shp") %>%
  clean_names() %>% 
  filter(statefp=="19") %>% 
  dplyr::rename(county_name_short=name, 
                county_fip=countyfp)

### add judicial district to iowa_geo_county based on county
iowa_county_shape %<>%
  mutate(judicial_district = case_when(
    county_name_short %in% district_1 ~ 1,
    county_name_short %in% district_2 ~ 2,
    county_name_short %in% district_3 ~ 3,
    county_name_short %in% district_4 ~ 4,
    county_name_short %in% district_5 ~ 5, 
    county_name_short %in% district_6 ~ 6, 
    county_name_short %in% district_7 ~ 7, 
    county_name_short %in% district_8 ~ 8, 
    TRUE ~ as.numeric(NA)),
    judicial_district = factor(judicial_district,
         levels = c(1,2,3,4,5,6,7,8),
         labels = c("District 1", "District 2", "District 3","District 4","District 5","District 6","District 7","District 8"))) %>% 
  mutate(judicial_district = as.numeric(judicial_district))

### use group_by and st_union to create district-level polygons using the county-level geography
### we'll use this district-level geography for additional lines to delineate groups of counties
iowa_district_shape <- iowa_county_shape %>%
  group_by(judicial_district) %>% 
  summarize(geometry = st_union(geometry))

### merge county shapefile to acs, census, and iowa data to attach geography and render the file map-able
### this will be the file we use to map
iowa_acs_census_county_geo <- merge(iowa_county_shape, iowa_acs_census_county_no_geo_rates, by = "county_name_short") %>% 
  mutate(percent_non_white = 100-percent_white,
         cdc_urban_rural_classification = factor(cdc_urban_rural_classification,
         levels = c("Rural Area","Town","Small City","Medium City")))  ### use factor function to assign labels to values
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### define color palettes for each layer in interactive map

### define palette for supervision_4_5_count_2020
pal_supervision_level_rate <- colorQuantile(palette = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"), domain = iowa_acs_census_county_geo$supervision_4_5_2020_rate_per_10000, n = 4, reverse = TRUE, na.color = "#808080") ### use reverse to invert colors 

### define palette for percent_non_white
pal_percent_race_non_white <- colorQuantile(palette = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"), domain = iowa_acs_census_county_geo$percent_non_white, n = 4, reverse = TRUE, na.color = "#808080") ### use reverse to invert colors 

### define palette for percent_black
pal_percent_race_black <- colorQuantile(palette = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"), domain = iowa_acs_census_county_geo$percent_black, n = 4, reverse = TRUE, na.color = "#808080") ### use reverse to invert colors 

### define palette for percent_black
pal_percent_race_white <- colorQuantile(palette = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"), domain = iowa_acs_census_county_geo$percent_white, n = 4, reverse = TRUE, na.color = "#808080") ### use reverse to invert colors 

### define palette for cdc_urban_rural_classification
pal_cdc_rural_urban <- colorFactor(palette = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"), domain = iowa_acs_census_county_geo$cdc_urban_rural_classification, reverse = TRUE, na.color = "#808080") ### use reverse to invert colors

# ### define palette for pre_to_post_covid_rate_change
# pal_revocation_rate <- colorQuantile(palette = c("#00475d","#007392","#0db4e4","#9ed4ef"), domain = iowa_acs_census_county_geo$pre_to_post_covid_rate_change, n = 4, reverse = TRUE) ### use reverse to invert colors
```




<br><br>
