---
title: "Mari/Sara To Do"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap","scales","raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","ragg","ggtext","csgjcr","distill","ezknitr")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE
  )
```

```{r include=FALSE}
### set theme
theme_set(theme_minimal())
```


## Questions:  

- Should LOS include PC holds? Weekends?  
- Do we need to determine which charges are sex, violent, or drug offense?  
- Interested in part 1 violent crimes? 

## Belknap:  

- Race categories: A, B, C, H, I, NH, O, P, U, W, X    
- Booking date range: 2018-07-01 - 2021-06-30  
- Housing: "Housed", "Unhoused"  
- No data: Ethnicity, release type, sentence status  

## Carroll:  

- Race categories: A, B, I, U, W   
- Booking date range: 2018-07-01 - 2021-06-30  
- Housing: "Housed", "Unhoused"  
- No data: Ethnicity  

## Cheshire:  

- Race categories: A, B, H, I, L, P, U, W   
- Booking date range: 2018-07-01 - 2021-06-29    
- Housing: All "Housed" - likely a data entry or excel issue  
- No data: Ethnicity, release type  

## Merrimack:  

- Race categories: A, B, H, I, O, P, U, W, X     
- Date range: 2018-07-01 - 2021-06-30   
- Housing: "Housed", "Unhoused", "Unknown"  
- No data: Ethnicity, release type  

